### 2020-01-19 paper/Ressourcen/Anfang.tex
adding the latex project for the paper based on TUM latex master. run with 'make'

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EINSTELLUNGEN
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\KOMAoptions{parskip=full}

% Seitenränder:

\newcommand{\SeitenrandOben}{25.8mm}
\newcommand{\SeitenrandRechts}{21mm}
\newcommand{\SeitenrandLinks}{40mm}
\newcommand{\SeitenrandUnten}{24.8mm}
\newcommand{\FusszeileHoehe}{11.7mm}

\usepackage[a4paper,
    head=0pt,
    top=\SeitenrandOben,
    bottom=\SeitenrandUnten,
    inner=\SeitenrandLinks,
    outer=\SeitenrandRechts
]{geometry}

% Fußzeilen:

\setlength{\footheight}{\FusszeileHoehe}
\clearscrheadfoot
\ifoot*{\Thema\vfill}
\ofoot*{\pagemark\vfill}
\setkomafont{pageheadfoot}{\fontsize{9pt}{13pt}\normalfont}
\setkomafont{pagefoot}{\bfseries}
\setkomafont{pagenumber}{\normalfont}
\pagestyle{scrheadings}

% Fußnoten:

\KOMAoptions{%
    footnotes=multiple % mehrere Fußnoten werden durch Zeichen getrennt
}
%\setfootnoterule[.6pt]{5.08cm}
\renewcommand{\footnoterule}{\hrule width 5.08cm height .6pt \vspace*{3.9mm}}
%\setlength{\footnotesep}{5mm}
\deffootnote{2mm}{2mm}{%
    \makebox[2mm][l]{\textsuperscript{\thefootnotemark}}%
}
\setkomafont{footnoterule}{\fontsize{9pt}{20pt}\selectfont}

% Überschriften:

\KOMAoptions{%
    open=any, % keine Festlegung auf linke oder rechte Seite
    numbers=noendperiod, % kein automatischer Punkt nach Gliederungsnummer
    headings=small
}

\makeatletter
\g@addto@macro{\@afterheading}{\vspace{-\parskip}} % \parskip nach Gliederungsbefehlen entfernen
\renewcommand*{\chapterheadstartvskip}{\vspace{\@tempskipa}\vspace{-3pt}} % Korrektur für Abstand über Kapitelüberschriften
\makeatother

\setkomafont{disposition}{\normalfont\sffamily}

\setkomafont{chapter}{\normalfont\fontsize{19pt}{22pt}\selectfont}
\RedeclareSectionCommand[%
  beforeskip=0pt,
  afterskip=29pt
]{chapter}
\renewcommand*{\chapterformat}{\thechapter.\enskip} % Immer Punkt nach Kapitelnummer

\setkomafont{section}{\fontsize{15pt}{17pt}\selectfont}
\RedeclareSectionCommand[%
  beforeskip=0pt,
  afterskip=24.1pt
]{section}
\renewcommand*{\sectionformat}{\makebox[13mm][l]{\thesection.\enskip}} % Feste Breite für Abschnittsnummer und immer Punkt danach

\setkomafont{subsection}{\bfseries\fontsize{12pt}{13pt}\selectfont}
\RedeclareSectionCommand[%
  beforeskip=0pt,
  afterskip=1pt
]{subsection}
\renewcommand*{\subsectionformat}{\makebox[13mm][l]{\thesubsection.\enskip}} % Feste Breite für Unterabschnittsnummer und immer Punkt danach

% Listen:

\setlist{%
    labelsep=0mm,
    itemindent=0pt,
    labelindent=0pt,
    align=left,
    parsep=1.5ex
}
\setlist[itemize]{%
    leftmargin=5mm,
    labelwidth=4.9mm
}
\setlist[itemize,1]{%
    before={\vspace{0.25ex}},
    label={\raisebox{.35ex}{\smaller[2]\textbullet}},
    after={\vspace{-\parsep}\vspace{-.25ex}}
}
\setlist[itemize,2]{%
    label={\raisebox{.35ex}{\rule{.58ex}{.58ex}}}
}
\setlist[enumerate]{%
    leftmargin=10mm,
    labelwidth=9.9mm
}
\setlist[enumerate,2]{%
    label={\alph*.}
}

\setlist[description]{%
%    labelindent=!,
    leftmargin=1em,
    labelwidth=!,
    parsep=0mm,
    partopsep=0mm,
    labelsep=1em,
}

% Verzeichnisse:

\KOMAoptions{%
    toc=flat, % keine Einrückungen im Inhaltsverzeichnis
    toc=chapterentrydotfill, % Punkte bis zur Seitennummer bei Kapiteln
    listof=entryprefix, % Präfix für Einträge in Abbildungs- und Tabellenverzeichnis
    listof=nochaptergap, % Kein Abstand für Kapiteleinträge in extra Verzeichnissen
}

\makeatletter
\renewcommand{\@dotsep}{.3} % Abstand der Füllpunkte

% "chapteratlist" für Inhaltsverzeichnis auswerten:
\renewcommand*{\addchaptertocentry}[2]{%
  \iftocfeature{toc}{chapteratlist}{}{%
    \addtocontents{toc}{\protect\vspace{-10pt}}% extra Abstand vor Kapitelüberschriften in Inhaltsverzeichnis entfernen
  }%
  % Originaldefinition aus scrbook.cls:
  \addtocentrydefault{chapter}{#1}{#2}%
  \if@chaptertolists
    \doforeachtocfile{%
      \iftocfeature{\@currext}{chapteratlist}{%
        \addxcontentsline{\@currext}{chapteratlist}[{#1}]{#2}%
      }{}%
    }%
    \@ifundefined{float@addtolists}{}{\scr@float@addtolists@warning}%
  \fi%
}
\makeatother

\AfterTOCHead[toc]{\protect\vspace{.8ex}} % Abstand zwischen Überschrift und Inhaltsverzeichnis
\setuptoc{toc}{noparskipfake} % Angleichung der Abstände nach Inhaltsverzeichnisüberschrift an andere Überschriften
\unsettoc{toc}{chapteratlist} % kein Abstand vor Kapiteleinträgen im Inhaltsverzeichnis, funktioniert nur durch obige Redefinition von \addchaptertocentry

% -- Abbildungs- und Tabellenverzeichnis:

\AfterTOCHead[lof]{\protect\vspace{-.1ex}\doublespacing} % Abstand zwischen Überschrift und Abbildungsverzeichnis, doppelter Zeilenabstand
\setuptoc{lof}{noparskipfake} % Angleichung der Abstände nach Abbildungsverzeichnisüberschrift an andere Überschriften

\AfterTOCHead[lot]{\protect\vspace{-.1ex}\doublespacing} % Abstand zwischen Überschrift und Tabellenverzeichnis, doppelter Zeilenabstand
\setuptoc{lot}{noparskipfake} % Angleichung der Abstände nach Tabellenverzeichnisüberschrift an andere Überschriften

% Beschriftungen:
\DeclareCaptionFormat{WissenschaftlicheArbeiten}{\fontsize{8pt}{10pt}\selectfont#1 #2#3\par}
\DeclareCaptionLabelFormat{WissenschaftlicheArbeiten}{\bfseries\selectfont#1 #2}

% -- Tabellen:
\captionsetup[table]{%
    format=WissenschaftlicheArbeiten,
    labelformat=WissenschaftlicheArbeiten,
    labelsep=none,
    singlelinecheck=off,
    justification=raggedright,
    skip=3pt,
    tablewithin=none
}

% -- Abbildungen:
\captionsetup[figure]{%
    format=WissenschaftlicheArbeiten,
    labelformat=WissenschaftlicheArbeiten,
    labelsep=none,
    singlelinecheck=off,
    justification=raggedright,
    skip=6.6mm,
    figurewithin=none
}

% Tabellen:
\renewcommand{\arraystretch}{1.8} % Skalierung der Tabellen
\newcolumntype{M}{X<{\vspace{4pt}}} % Spaltentyp mit Abstand rechts

% Glossare & Abkürzungsverzeichnis:

\makeglossaries
\input{Abkuerzungen}
\setacronymstyle{short-long}

\makeatletter
\newlength{\@glsdotsep}
\setlength{\@glsdotsep}{\@dotsep em}
\newcommand*{\glsdotfill}{\leavevmode \cleaders \hb@xt@ \@glsdotsep{\hss .\hss }\hfill \kern \z@}
\makeatother

\newglossarystyle{WissenschaftlicheArbeiten}{%
  \setglossarystyle{index}%

  \renewcommand*{\glossaryheader}{\vspace{.75em}}%
  \renewcommand*{\glstreenamefmt}[1]{##1}%
  \renewcommand*{\glossentry}[2]{%
     \item\glsentryitem{##1}\glstreenamefmt{\glstarget{##1}{\glossentryname{##1}}}%
     \ifglshassymbol{##1}{\space(\glossentrysymbol{##1})}{}%
     \space-\space\glossentrydesc{##1}\glsdotfill\glspostdescription\space ##2%
  }%
  \renewcommand*{\glsgroupheading}[1]{%
    \item\glstreenamefmt{\textbf{\fontsize{14}{17}\selectfont\enskip\glsgetgrouptitle{##1}}}\vspace{.3em}}%
}

\setglossarystyle{WissenschaftlicheArbeiten}

### 2020-01-19 paper/WissenschaftlicheArbeit.tex
adding the latex project for the paper based on TUM latex master. run with 'make'

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TUM-Vorlage: Wissenschaftliche Arbeit
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Rechteinhaber:
%     Technische Universität München
%     https://www.tum.de
% 
% Gestaltung:
%     ediundsepp Gestaltungsgesellschaft, München
%     http://www.ediundsepp.de
% 
% Technische Umsetzung:
%     eWorks GmbH, Frankfurt am Main
%     http://www.eworks.de
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{./Ressourcen/Praeambel.tex} % !!! NICHT ENTFERNEN !!!
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\renewcommand{\Thema}{%
    Thema der Arbeit (optional)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{./Ressourcen/Anfang.tex} % !!! NICHT ENTFERNEN !!!
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\title{Thema der Arbeit}
\author{Martin Mustermann}
\date{Datum}

\tableofcontents % Inhaltsverzeichnis

\chapter{Kapitelüberschrift}

\section{Unterkapitelüberschrift}

\subsection[]{Absatzüberschrift}

Dies ist die Vorlage für eine wissenschaftliche Arbeit nach dem Corporate
Design der Technischen Universität München (TUM). Die Vorlage ist für "`TeX
Live 2015"' kompatibel.

Bitte geben Sie Ihren individuellen Text an den vorgesehenen Stellen ein und
beachten Sie die Formatvorgaben des jeweiligen Lehrstuhls oder der Prüfenden
zum inhaltlichen und formalen Aufbau der wissenschaftlichen Arbeit. Achten Sie
grundsätzlich auf ein angenehmes Erscheinungsbild für den Leser und dass ein
1,5-facher Zeilenabstand und am Rand genügend Platz für Korrekturen
eingehalten wird\footnote{Bitte beachten Sie die Zitationsvorgaben Ihres
Prüfers.}.

Grundsätzlich sind die Schriftarten Arial und Times New Roman, sowie die Neue
Helvetica zulässig. Der Text ist links ausgerichtet und in Blocksatz gesetzt.
Auszeichnungen der Schrift können durch Fettung, Schrägstellung und
Unterstreichung erfolgen. Farbige Schrift sollte nur in Ausnahmefällen oder
Grafiken zum Einsatz kommen.

\begin{figure}[!ht]
\noindent\hspace{0.5mm}\includegraphics[width=12cm]{./Ressourcen/Desert.jpg}
\caption{Titel, Autor}
\end{figure}

\clearpage

Passen Sie gegebenenfalls die Ränder an die Vorgaben Ihres Prüfers an und
beachten Sie dabei, dass das Logo der TUM sich oben rechts innerhalb der
Ränder, auf der Titelseite befindet. Für die Titelseiten stehen separate
Vorlagen zur Verfügung.

Zur Definition von \gls{abk} erstellen Sie für die gewünschte Abkürzung einen
Eintrag in der Datei \texttt{Abkuerzungen.tex} und referenzieren sie ihn
mittels \texttt{\textbackslash{}gls}; diese tauchen nach einem Lauf mit
\texttt{latexmk} im Abkürzungsverzeichnis auf. Beispiel:

\vspace{-\baselineskip}
\begin{description}[leftmargin=1em+5mm, labelindent=5mm]
\item[Definition in \texttt{Abkuerzungen.tex}:] \texttt{\textbackslash{}newacronym\{abk\}\{Abk.\}\{Abkürzungen\}\}}
\item[Referenzierung:] \texttt{\textbackslash{}gls\{abk\}}
\end{description}

Für weitere Informationen zu Glossaren und Abkürzungen siehe die Dokumentation
des Pakets \texttt{glossaries} und die entsprechenden Abschnitte in den
Vorlagendateien.

\subsection[]{Aufzählungen}

\begin{itemize}
\item Dies ist die Standardaufzählung
    \begin{itemize}
    \item Dies ist die nächste Ebene der Aufzählung
    \end{itemize}
\end{itemize}

\subsection[]{Nummerierungen}

\begin{enumerate}
\item Erster Punkt der Nummerierungen
    \begin{enumerate}
    \item Unterpunkt der Nummerierungen
    \end{enumerate}
\end{enumerate}
\clearpage

\listoffigures % Abbildungsverzeichnis

\printacronyms[title={Abkürzungsverzeichnis}] % Abkürzungsverzeichnis

\listoftables % Tabellenverzeichnis

\onehalfspacing

\addchap{Tabellenvarianten}

\vspace{22mm}
\section*{Überschrift Tabelle 1}

\begin{table}[!h]
\begin{tabularx}{\textwidth + 5pt}{@{\hspace{3pt}} M | @{\hspace{3pt}} M}
\multicolumn{2}{@{}X}{%
    \begin{tabularx}{\textwidth}{@{\hspace{3pt}} M @{\hspace{14.5pt}} M}
    \textbf{Spalte 1} & \textbf{Spalte 2}
    \end{tabularx}%
} \\
\hline
Nummer 1 & Nummer 2 \\
\hline
Nummer 1 & Nummer 2 \\
\hline
Nummer 1 & Nummer 2 \\
\hline
\end{tabularx}

\caption{Beschreibung}
\end{table}

\vspace{\parskip}
\section*{Überschrift Tabelle 2}

\begin{table}[!h]
\hspace{-5pt}
\begin{tabularx}{\textwidth + 5pt}{| @{\hspace{3pt}} M | @{\hspace{3pt}} M |}
\hline
\textbf{Spalte 1} & \textbf{Spalte 2} \\
\hline
Nummer 1 & Nummer 2 \\
\hline
Nummer 1 & Nummer 2 \\
\hline
Nummer 1 & Nummer 2 \\
\hline
\end{tabularx}
\caption{}
\end{table}

\vspace{\parskip}
\section*{Überschrift Tabelle 3}

\begin{table}[!h]
\begin{tabularx}{\textwidth}{@{} M M}
\textbf{Spalte 1} & \textbf{Spalte 2} \\
Nummer 1 & Nummer 2 \\
Nummer 1 & Nummer 2 \\
Nummer 1 & Nummer 2 \\
\end{tabularx}
\caption{}
\end{table}

\clearpage

\addchap{Tabellenvarianten 2}

\vspace{22mm}
\section*{Überschrift Tabelle 1}

\begin{table}[!h]
\fontsize{9pt}{13pt}\selectfont
%\renewcommand{\arraystretch}{1.8}
\hspace{-5pt}
\begin{tabularx}{\textwidth + 5pt}{@{\hspace{3pt}} M | @{\hspace{3pt}} M}
\multicolumn{2}{@{}X}{%
    \begin{tabularx}{\textwidth}{@{\hspace{3pt}} M @{\hspace{14.5pt}} M}
    \textbf{Spalte 1} & \textbf{Spalte 2}
    \end{tabularx}%
} \\
\hline
Nummer 1,\newline\,mehrzeilig in Schriftgröße 9 pt & Nummer 2 \\
\hline
Nummer 1 & Nummer 2 \\
\hline
Nummer 1 & Nummer 2 \\
\hline
\end{tabularx}

\caption{}
\end{table}

\vspace{\parskip}
\section*{Überschrift Tabelle 2}

\begin{table}[!h]
\fontsize{9pt}{13pt}\selectfont
\hspace{-5pt}
%\renewcommand{\arraystretch}{1.8}
\begin{tabularx}{\textwidth + 5pt}{| @{\hspace{3pt}} M | @{\hspace{3pt}} M |}
\hline
\textbf{Spalte 1} & \textbf{Spalte 2} \\
\hline
Nummer 1 & Nummer 2 \\
\hline
Nummer 1 & Nummer 2 \\
\hline
Nummer 1 & Nummer 2 \\
\hline
\end{tabularx}
\caption{}
\end{table}

\vspace{\parskip}
\section*{Überschrift Tabelle 3}

\begin{table}[!h]
\fontsize{9pt}{13pt}\selectfont
%\renewcommand{\arraystretch}{1.8}
\begin{tabularx}{\textwidth}{@{} M M}
\textbf{Spalte 1} & \textbf{Spalte 2} \\
Nummer 1 & Nummer 2 \\
Nummer 1 & Nummer 2 \\
Nummer 1 & Nummer 2 \\
\end{tabularx}
\caption{}
\end{table}

\end{document}

### 2020-01-21 analysis/analyze.py
creating a network with dist

@@ -3,23 +3,39 @@ import numpy as np
 import networkx as nx
 import matplotlib.pyplot as plt
 import sqlite3
-
+import geopy.distance
 
 routes = nx.MultiDiGraph()
 
 conn = sqlite3.connect('../fghjij.db')
 cursor = conn.cursor()
 
-cursor.execute("SELECT * FROM routes WHERE airline_id='4066'")
+cursor.execute("SELECT * FROM routes limit 100")
 
 rows = cursor.fetchall()
+
+
+def get_dist(orig, dest):
+    coord = []
+    cursor.execute("SELECT * from airports WHERE iata=? OR iata=?", (dest, orig))
+    airports = cursor.fetchall()
+    for airport in airports:
+        coord.append((airport[6], airport[7]))
+    if len(airports) == 2:
+        return geopy.distance.vincenty(coord[0], coord[1]).km
+    else:
+        return 100
+
+
 for row in rows:
-    routes.add_edge(row[3], row[5])
+    if not routes.has_edge(row[2], row[4], key=row[1]):
+        dist = get_dist(row[2], row[4])
+        routes.add_edge(row[2], row[4], key=row[1], dist=dist)
 
 # with open('../data/routes.dat') as f:
 #     csv_reader = csv.reader(f)
 #     for row in csv_reader:
 #         routes.add_edge(row[3], row[5])
 
-nx.draw_networkx(routes)
-plt.show()
+nx.draw_networkx(routes, with_labels=True, node_size=10, font_size=2, arrowsize=4)
+plt.savefig("./sample3.pdf", bbox_inches='tight', format='pdf', dpi=1200)

### 2020-02-05 scripts/analyze.py
removing unnecessary imports

@@ -1,4 +1,3 @@
-import csv
 import numpy as np
 import networkx as nx
 import matplotlib.pyplot as plt
@@ -28,11 +27,6 @@ def getEntireNetwork():
         if not routes.has_edge(row[2], row[4], key=row[1]):
             dist = get_dist(row[2], row[4])
             routes.add_edge(row[2], row[4], key=row[1], dist=dist)
-
-    # with open('../data/routes.dat') as f:
-    #     csv_reader = csv.reader(f)
-    #     for row in csv_reader:
-    #         routes.add_edge(row[3], row[5])
 
     nx.draw_networkx(routes, with_labels=True, node_size=10, font_size=2, arrowsize=4)
     plt.savefig("./sample3.pdf", bbox_inches='tight', format='pdf', dpi=1200)

### 2020-02-05 scripts/analyze.py
renamed analyze.py to network_loaders.py refactored loadAirlineNetwork

@@ -1,61 +1,0 @@
-import numpy as np
-import networkx as nx
-import matplotlib.pyplot as plt
-import sqlite3
-import geopy.distance
-
-
-def getEntireNetwork():
-    routes = nx.MultiDiGraph()
-    conn = sqlite3.connect('../fghjij.db')
-    cursor = conn.cursor()
-    cursor.execute("SELECT * FROM routes limit 100")
-    rows = cursor.fetchall()
-
-    def get_dist(orig, dest):
-        coord = []
-        cursor.execute("SELECT * from airports WHERE iata=? OR iata=?", (dest, orig))
-        airports = cursor.fetchall()
-        for airport in airports:
-            coord.append((airport[6], airport[7]))
-        if len(airports) == 2:
-            return geopy.distance.vincenty(coord[0], coord[1]).km
-        else:
-            return 100  # just a random distance when sometimes we dont have the coords of the airport
-
-    for row in rows:
-        if not routes.has_edge(row[2], row[4], key=row[1]):
-            dist = get_dist(row[2], row[4])
-            routes.add_edge(row[2], row[4], key=row[1], dist=dist)
-
-    nx.draw_networkx(routes, with_labels=True, node_size=10, font_size=2, arrowsize=4)
-    plt.savefig("./sample3.pdf", bbox_inches='tight', format='pdf', dpi=1200)
-    return routes
-
-
-def getAirlineNetwork(airline_code):
-    routes = nx.MultiDiGraph()
-    conn = sqlite3.connect('../fghjij.db')
-    cursor = conn.cursor()
-    cursor.execute("SELECT * FROM routes where airline_id=?", (airline_code,))
-    rows = cursor.fetchall()
-
-    def get_dist(orig, dest):
-        coord = []
-        cursor.execute("SELECT * from airports WHERE iata=? OR iata=?", (dest, orig))
-        airports = cursor.fetchall()
-        for airport in airports:
-            coord.append((airport[6], airport[7]))
-        if len(airports) == 2:
-            return geopy.distance.vincenty(coord[0], coord[1]).km
-        else:
-            return 100  # just a random distance when sometimes we dont have the coords of the airport
-
-    for row in rows:
-        if not routes.has_edge(row[2], row[4], key=row[1]):
-            dist = get_dist(row[2], row[4])
-            routes.add_edge(row[2], row[4], key=row[1], dist=dist)
-
[…]

### 2020-02-05 scripts/network_loaders.py

@@ -1,0 +1,61 @@
+import networkx as nx
+import matplotlib.pyplot as plt
+import sqlite3
+import geopy.distance
+
+# local modules
+import local_config
+
+def getEntireNetwork():
+	routes = nx.MultiDiGraph()
+	conn = sqlite3.connect(local_config.db_file)
+	cursor = conn.cursor()
+	cursor.execute("SELECT * FROM routes limit 100")
+	rows = cursor.fetchall()
+
+	def get_dist(orig, dest):
+		coord = []
+		cursor.execute("SELECT * from airports WHERE iata=? OR iata=?", (dest, orig))
+		airports = cursor.fetchall()
+		for airport in airports:
+			coord.append((airport[6], airport[7]))
+		if len(airports) == 2:
+			return geopy.distance.vincenty(coord[0], coord[1]).km
+		else:
+			return 100  # just a random distance when sometimes we dont have the coords of the airport
+
+	for row in rows:
+		if not routes.has_edge(row[2], row[4], key=row[1]):
+			dist = get_dist(row[2], row[4])
+			routes.add_edge(row[2], row[4], key=row[1], dist=dist)
+
+	nx.draw_networkx(routes, with_labels=True, node_size=10, font_size=2, arrowsize=4)
+	plt.savefig("./sample3.pdf", bbox_inches='tight', format='pdf', dpi=1200)
+	return routes
+
+def loadAirlineNetwork(airline_id):
+	G = nx.DiGraph()
+	conn = sqlite3.connect(local_config.db_file)
+	cursor = conn.cursor()
+
+	route_columns = [
+		"source_airport_id", 
+		"destination_airport_id", 
+		"airline_id",
+		"geo_distance", 
+		"passenger_flow"
+	]
+
+	query = "SELECT {} FROM routes WHERE airline_id=?".format(', '.join(route_columns))
+
+	cursor.execute(query, [airline_id])
+
+	for row in cursor: 
+		sa_id = row[0]
+		da_id = row[1]
+		attribs = {}
+		for column_name in route_columns[2:]:
+			attribs[column_name] = column_name
+		G.add_edge(sa_id, da_id, attr_dict=attribs)
+
+	return G

### 2020-02-05 scripts/network_loaders.py
adding aiport info to the airline graph

@@ -54,8 +54,29 @@ def loadAirlineNetwork(airline_id):
 		sa_id = row[0]
 		da_id = row[1]
 		attribs = {}
+		column_index = 2
 		for column_name in route_columns[2:]:
-			attribs[column_name] = column_name
+			attribs[column_name] = row[column_index]
+			column_index += 1
 		G.add_edge(sa_id, da_id, attr_dict=attribs)
+
+	# add airport information to relevant nodes
+	airport_columns = [
+		"airport_id",
+		"name", 
+		"iata", 
+		"icao", 
+		"city", 
+		"country", 
+		"latitude", 
+		"longitude", 
+		"patronage",
+	]
+	cursor.execute('SELECT {0} FROM airports'.format(', '.join(airport_columns)))
+	for row in cursor:
+		a_id = row[0]
+		if a_id in G.nodes:
+			for column_index, column_name in enumerate(airport_columns): 
+				G.nodes[a_id][column_name] = row[column_index]
 
 	return G

### 2020-02-05 scripts/largeness-example.py
implementing the largness function for airline networks, + one example calculation

@@ -1,0 +1,24 @@
+import networkx as nx
+import sqlite3
+import matplotlib.pyplot as plt
+
+# local modules
+from network_loaders import loadAirlineNetwork
+import largeness
+
+G_lufthansa = loadAirlineNetwork('3320')
+G_airfrance = loadAirlineNetwork('137')
+
+l_lufthansa = largeness.calculateForGraph(G_lufthansa)
+print('lufthansa largeness', l_lufthansa)
+l_airfrance = largeness.calculateForGraph(G_airfrance)
+print('airfrance largeness', l_airfrance)
+
+G_both = nx.compose(G_lufthansa, G_airfrance)
+l_both = largeness.calculateForGraph(G_both)
+print('joint largeness', l_both)
+
+print('cooperation opportunity', (l_lufthansa + l_airfrance ) /  l_both)
+
+# nx.draw(G) 
+# plt.show()

### 2020-02-05 scripts/largeness.py

@@ -1,0 +1,22 @@
+import networkx as nx
+import numpy as np
+import math
+
+
+
+def calculateForGraph(G): 
+	nodes = list(G.nodes())
+	adjm = nx.to_numpy_matrix(G, dtype=int, multigraph_weight='min')	
+
+	square = np.linalg.matrix_power(adjm, 2) 
+	
+	(n, m) = np.shape(square) 
+	largeness = 0
+	for i in range(n): 
+		for j in range(m): 
+			if square[i,j] > 0: #and adjm[i,j] = 0 just an idea
+				sa_node = G.nodes[nodes[i]]
+				da_node = G.nodes[nodes[j]]
+				largeness += math.sqrt(sa_node["patronage"] * da_node["patronage"])
+
+	return largeness

### 2020-02-05 scripts/load_from_db.py
adding deletion of about 500 routes which don't have an airline value

@@ -37,7 +37,6 @@ def load(db_file=local_config.db_file):
 	for row in db_cursor:
 		airline_id = row[0]
 		airlines[airline_id] = Airline(*row)
-	airlines['\\N'] = Airline('\\N', 'unknown airline', '', '')
 
 	route_columns = [
 		"airline_id",

### 2020-02-05 scripts/estimate-passenger-flows.py
also loading flow_sum and flow_deviation into the db

@@ -112,7 +112,7 @@ def run(db_file):
 				route.destination_airport.airport_id,
 				route.flow
 			))
-		airport_csv = open('./temp_airport_flow_deviation.csv', 'w')
+		airport_csv = open('./temp_flow_estimation_metrics.csv', 'w')
 		for airport_id, airport in airports.items():
 			airport_csv.write("%s,%f,%f\n" % (
 				airport_id, 

### 2020-02-05 setup-db.sh

@@ -43,8 +43,9 @@ python ./scripts/estimate-passenger-flows.py write_csv "$DB_FILE"
 
 printf "adding passenger flows"
 sqlite3 "$DB_FILE" < ./queries/set-up-passenger-flows.sql
+sqlite3 "$DB_FILE" < ./queries/set-up-flow-estimation-metrics.sql
 rm ./temp_passenger_flows.csv
-rm ./temp_airport_flow_deviation.csv
+rm ./temp_flow_estimation_metrics.csv
 
 printf "\ndone, enjoy.\n\n" 
 

### 2020-02-05 scripts/largeness-example.py
choose your own airports by command line params in the largeness-example

@@ -1,24 +1,31 @@
 import networkx as nx
 import sqlite3
 import matplotlib.pyplot as plt
+import sys
 
 # local modules
 from network_loaders import loadAirlineNetwork
 import largeness
 
-G_lufthansa = loadAirlineNetwork('3320')
-G_airfrance = loadAirlineNetwork('137')
+A_id = '3320'
+B_id = '137'
+if(len(sys.argv) == 3):
+	A_id = sys.argv[1] 
+	B_id = sys.argv[2]
 
-l_lufthansa = largeness.calculateForGraph(G_lufthansa)
-print('lufthansa largeness', l_lufthansa)
-l_airfrance = largeness.calculateForGraph(G_airfrance)
-print('airfrance largeness', l_airfrance)
+G_A = loadAirlineNetwork(A_id)
+G_B = loadAirlineNetwork(B_id)
 
-G_both = nx.compose(G_lufthansa, G_airfrance)
+l_A = largeness.calculateForGraph(G_A)
+print('A largeness', l_A)
+l_B = largeness.calculateForGraph(G_B)
+print('B largeness', l_B)
+
+G_both = nx.compose(G_A, G_B)
 l_both = largeness.calculateForGraph(G_both)
 print('joint largeness', l_both)
 
-print('cooperation opportunity', (l_lufthansa + l_airfrance ) /  l_both)
+print('cooperation opportunity', l_both / (l_A + l_B ))
 
 # nx.draw(G) 
 # plt.show()

### 2020-02-05 scripts/network_loaders.py
implementing a script that shows the distance 3 neighbors of a node - nice for manual investigations

@@ -33,23 +33,61 @@ def getEntireNetwork():
 	plt.savefig("./sample3.pdf", bbox_inches='tight', format='pdf', dpi=1200)
 	return routes
 
+
+airport_columns = [
+	"airport_id",
+	"name", 
+	"iata", 
+	"icao", 
+	"city", 
+	"country", 
+	"latitude", 
+	"longitude", 
+	"patronage",
+]
+
+
+route_columns = [
+	"source_airport_id", 
+	"destination_airport_id", 
+	"airline_id",
+	"geo_distance", 
+	"passenger_flow"
+]
+
+
+def loadEntireNetwork(): 
+	G = nx.MultiDiGraph()
+	conn = sqlite3.connect(local_config.db_file)
+	cursor = conn.cursor()
+
+	cursor.execute('SELECT {0} FROM airports'.format(','.join(airport_columns)))
+	for row in cursor: 
+		a_id = row[0]
+		attribs = {}
+		for column_index, column_name in enumerate(airport_columns): 
+			attribs[column_name] = row[column_index]
+		G.add_node(a_id, **attribs)	
+		
+	cursor.execute('SELECT {0} FROM routes'.format(','.join(route_columns)))
+	for row in cursor: 
+		sa_id = row[0]
+		da_id = row[1]
+		attribs = {}
+		for column_index, column_name in enumerate(route_columns): 
+			attribs[column_name] = row[column_index]
+		G.add_edge(sa_id, da_id, **attribs)
+	
+	return G
+
+
 def loadAirlineNetwork(airline_id):
 	G = nx.DiGraph()
 	conn = sqlite3.connect(local_config.db_file)
 	cursor = conn.cursor()
 
-	route_columns = [
-		"source_airport_id", 
-		"destination_airport_id", 
-		"airline_id",
-		"geo_distance", 
-		"passenger_flow"
-	]
-
 	query = "SELECT {} FROM routes WHERE airline_id=?".format(', '.join(route_columns))
-
 	cursor.execute(query, [airline_id])
-
 	for row in cursor: 
 		sa_id = row[0]
 		da_id = row[1]
@@ -58,20 +96,8 @@ def loadAirlineNetwork(airline_id):
 		for column_name in route_columns[2:]:
 			attribs[column_name] = row[column_index]
 			column_index += 1
-		G.add_edge(sa_id, da_id, attr_dict=attribs)
+		G.add_edge(sa_id, da_id, **attribs)
 
[…]

### 2020-02-05 scripts/show-ego-net.py

@@ -1,0 +1,25 @@
+import sys
+import networkx as nx
+import matplotlib.pyplot as plt
+
+# local modules
+import network_loaders
+
+n = '10'
+if len(sys.argv) < 2: 
+	print("Usage: {0} <airport_id>".format(sys.argv[0]))
+	print("Now using default node {0}".format(n))
+else:
+	n = sys.argv[1]
+
+G = network_loaders.loadEntireNetwork()
+
+S = nx.ego_graph(G, n, radius=3, undirected=True) 
+
+nx.draw(
+	S,
+	labels={k: "%s:\n%s\nptrn:%i\n\n\n\n" % (k, S.nodes[k]["name"], S.nodes[k]["patronage"]) for k in S.nodes},
+	node_color=['#993322' if n == k else '#4477ee' for k in S.nodes],
+	node_size=100
+)
+plt.show()

### 2020-02-05 scripts/largeness.py
rmving white space

@@ -2,8 +2,6 @@ import networkx as nx
 import numpy as np
 import math
 
-
-
 def calculateForGraph(G): 
 	nodes = list(G.nodes())
 	adjm = nx.to_numpy_matrix(G, dtype=int, multigraph_weight='min')	

### 2020-02-06 scripts/estimate-patronage-based-on-neighbor-airport-patronages.py
started work on improving missing patronage estimation based on neighboring airports

@@ -1,0 +1,3 @@
+import sqlite
+
+

### 2020-02-06 setup-db.sh

@@ -27,6 +27,7 @@ cp ./airport-patronage/estimated-2014-patronage.csv ./data/
 
 printf "adding patronage column...\n"
 sqlite3 "$DB_FILE" < ./queries/set-up-patronage.sql
+python ./scripts/estimate-patronage-based-on-neighbor-airport-patronages.py "$DB_FILE"
 
 printf "removing duplicate routes (source, destination, airline)...\n"
 sqlite3 "$DB_FILE" < ./queries/remove-duplicate-connections-by-same-airline.sql

### 2020-02-07 scripts/draw-nodes-on-map.py
printing subgraphs and drawing them on a map

@@ -1,0 +1,53 @@
+import sqlite3
+import sys
+import networkx as nx
+import plotly.graph_objects as go
+
+# local modules
+import network_loaders
+
+airport_ids = sys.argv[1:]
+
+if len(airport_ids) > 0: 
+	G = network_loaders.loadEntireNetwork()
+
+	S = G.subgraph(airport_ids)
+
+	fig = go.Figure()
+
+	marker = dict(
+		size=10,
+		color='rgb(255,0,0)'
+	)
+	for airport_id in S.nodes:
+		airport = S.nodes[airport_id]
+		fig.add_trace(go.Scattergeo(
+			lon=[float(airport["longitude"])],
+			lat=[float(airport["latitude"])],
+			text=airport["name"],
+			mode='markers',
+			marker=marker
+		))
+
+	for edge in S.edges: 
+		sa = S.nodes[edge[0]]
+		da = S.nodes[edge[1]]
+		fig.add_trace(go.Scattergeo(
+			lon=[sa["longitude"], da["longitude"]],
+			lat=[sa["latitude"], da["latitude"]],
+			mode='lines',
+			line=dict(width=1, color='red')
+		))
+
+	fig.update_layout(
+		geo=go.layout.Geo(),
+		height=700
+	)
+	fig.update_geos(
+		resolution=50, 
+		projection_type='orthographic'
+	)
+
+	fig.show()
+else:
+	print("Usage: %s <airport_id 1> <airport_id 2> ... <airport_id n>" % sys.argv[0])

### 2020-02-07 scripts/print-subgraphs.py

@@ -1,0 +1,16 @@
+import networkx as nx
+
+import network_loaders 
+
+G = network_loaders.loadEntireNetwork()
+
+G = nx.to_undirected(G)
+
+connected_subgraphs = nx.connected_components(G)
+
+for i, S in enumerate(connected_subgraphs): 
+	print("Subgraph", i) 
+	print("Number of nodes:", S)
+	print(' '.join(list(S)))
+
+

### 2020-02-07 paper/main.tex
adding section headlines, subgraph situation description and this paper on which the largeness idea is based on

%%
% TUM Corporate Design LaTeX Templates
% Based on the templates from https://www.tum.de/cd
%
% Feel free to join development on
% https://gitlab.lrz.de/tum-templates/templates
% and/or to create an issue in case of trouble.
%
% tum-article class for scientific articles, reports, exercise sheets, ...
%
%%

\documentclass[twocolumn]{tum-article}
%\documentclass[twocolumn, german]{tum-article}
%\documentclass[times, twocolumn]{tum-article}
%\documentclass[times]{tum-article}
%\documentclass{tum-article}

%\usepackage{lipsum}

\title{Analysis of the 2014 Passenger Flight Network}
\author{Felix Paul Niemeyer\authormark{1},
	Saicharan Kumar\authormark{2}}
% Author 3\authormark{1}\orcid{0000-0000-0000-0000}}

% if too long for running head
\titlerunning{TUM Article}
\authorrunning{Author 1 et al.}

%\email{niemeyer.felix@tum.de}

\affil[1]{felix.niemeyer@tum.de, MiM}
\affil[2]{saicharan.kumar@tum.de, MiM}

\date{Received: 19.02.2020 - This is work in progress}

\begin{document}

\maketitle

\begin{abstract}
	In this case study we are looking at a dataset about air travel in 2014. We implement some mechanisms to clean the data, as well as mechanisms to enrich this dataset with information we query from wikidata. We estimate some missing data. Starting from there, we analyze some network characteristics for the whole network as well as airline-specific sub-networks. We compare airline-specific networks and find relations between their network's characteristics and their business model. We propose one metric that plays a role in forcasting whether a cooperation between two airlines is advantageous and use this metric to generate an alliances landscape. We compare it's predictive correctness to the real world by looking at the formation of Vanilla Airlines which occured in the year after the one our data stems from. 
\end{abstract}

\section{Data Description}

example cite \cite{jirauschek20141}

\section{Data Enrichment \& Estimation}

\section{Basic Network Analysis}
There are 7 disconnected subgraphs in the Graph.
Besides the main network, that includes ... nodes, there are 6 small ones with only a couple of nodes.
One with 10 nodes for example, consists only of airports that are located in New Caledonia, an archipelago in the Pacific Ocean. 
Another disconnected subgraph represents the connection of four airports around the San Juan Islands, an archipelago in the Pacific Northwest of the United States. There are two more disconnected subgraphs with four nodes and two with only two nodes.

<images of these networks drawn on a map>

\section{Airline Subnetwork Analysis \& Comparison}

The possibility to provide convenient on-line connections to clients is an important factor that drives welfare gains through ailine cooperation according to E. E. Bailey and D. Liu \cite{airline_consolidation_and_consumer_welfare}.
\section{Airline Cooperation Opportunity}

\section{Reality Check: Vanilla Airlines}

\section*{Acknowledgements}

\bibliographystyle{IEEEtran}
\bibliography{literature}

\end{document}

### 2020-02-07 scripts/estimate-missing-patronage.py
estimating patronage based on neighbors

@@ -1,0 +1,51 @@
+import sqlite3
+import sys
+import networkx as nx
+
+# local modules
+import network_loaders 
+
+if len(sys.argv) < 3: 
+	print("Usage: {0} <db-file> <output-file>".format(sys.argv[0]))
+else:
+
+	G = network_loaders.loadEntireNetwork(
+		airport_columns=["patronage"],
+		route_columns=[], 
+		db_file=sys.argv[1]
+	)
+
+	nodes = G.nodes
+
+	of = open(sys.argv[2], 'w') 
+
+	previous_remaining = -1
+	remaining = 0
+	while remaining != previous_remaining:
+		previous_remaining = remaining
+		remaining = 0
+		estimated_patronages = {}
+		for airport_id in nodes:
+			node = nodes[airport_id]
+			if node["patronage"] == None:
+				neighbors = G.neighbors(airport_id) 
+				node_degree = G.degree(airport_id)
+				estimation_sum = 0
+				count = 0
+				for neighbor_id in neighbors: 
+					neighbor = nodes[neighbor_id]
+					if neighbor["patronage"] != None: 
+						estimation_sum += node_degree * neighbor["patronage"] / G.degree(neighbor_id)
+						count += 1
+				if count == 0:
+					remaining += 1
+				else:
+					estimation_avg = estimation_sum / count
+					estimated_patronages[airport_id] = estimation_avg
+		for airport_id in estimated_patronages: 
+			nodes[airport_id]["patronage"] = estimated_patronages[airport_id]
+			line = "%s,%i\n" % (airport_id, estimated_patronages[airport_id])
+			of.write(line)
+			#print(line)
+	
+	of.flush()	

### 2020-02-07 scripts/estimate-patronage-based-on-neighbor-airport-patronages.py

@@ -1,3 +1,0 @@
-import sqlite
-
-

### 2020-02-07 setup-db.sh
adapting setup script, another load query

@@ -12,9 +12,6 @@ printf "loading and cleaning openflights data...\n"
 sqlite3 "$DB_FILE" < ./queries/load-openflights-data.sql 
 sqlite3 "$DB_FILE" < ./queries/clean-openflights-data.sql
 
-printf "adding runway surface column\n"
-sqlite3 "$DB_FILE" < ./queries/set-up-runway-surface.sql
-
 printf "exporting airport list...\n" 
 sqlite3 "$DB_FILE" < ./queries/list-airports.sql > ./airport-patronage/custom_airport_ids
 
@@ -27,7 +24,12 @@ cp ./airport-patronage/estimated-2014-patronage.csv ./data/
 
 printf "adding patronage column...\n"
 sqlite3 "$DB_FILE" < ./queries/set-up-patronage.sql
-python ./scripts/estimate-patronage-based-on-neighbor-airport-patronages.py "$DB_FILE"
+
+printf "estimating missing patronage...\n"
+python ./scripts/estimate-missing-patronage.py "$DB_FILE" ./temp_patronages_estimations.csv
+
+printf "loading missing patronage estimations...\n"
+sqlite3 "$DB_FILE" < ./queries/load-missing-patronage-estimations.sql
 
 printf "removing duplicate routes (source, destination, airline)...\n"
 sqlite3 "$DB_FILE" < ./queries/remove-duplicate-connections-by-same-airline.sql
@@ -49,4 +51,5 @@ rm ./temp_passenger_flows.csv
 rm ./temp_flow_estimation_metrics.csv
 
 printf "\ndone, enjoy.\n\n" 
+
 

### 2020-02-07 setup-db.sh
fixes, renamings

@@ -26,10 +26,14 @@ printf "adding patronage column...\n"
 sqlite3 "$DB_FILE" < ./queries/set-up-patronage.sql
 
 printf "estimating missing patronage...\n"
-python ./scripts/estimate-missing-patronage.py "$DB_FILE" ./temp_patronages_estimations.csv
+python ./scripts/estimate-missing-patronages.py "$DB_FILE" ./temp_missing_patronages.csv
 
 printf "loading missing patronage estimations...\n"
 sqlite3 "$DB_FILE" < ./queries/load-missing-patronage-estimations.sql
+rm ./temp_missing_patronages.csv
+
+printf "applying default patronage to remaining airports...\n"
+sqlite3 "$DB_FILE" < ./queries/apply-default_patronage.sql
 
 printf "removing duplicate routes (source, destination, airline)...\n"
 sqlite3 "$DB_FILE" < ./queries/remove-duplicate-connections-by-same-airline.sql

### 2020-02-07 scripts/estimate-missing-patronages.py
taking undirected neighbors into account for patronage estmiation

@@ -15,6 +15,8 @@ else:
 		db_file=sys.argv[1]
 	)
 
+	G = G.to_undirected(reciprocal=False)
+
 	nodes = G.nodes
 
 	of = open(sys.argv[2], 'w') 

### 2020-02-07 scripts/show-ego-net.py
removing disconnected airports with no patronage information from the data

@@ -14,7 +14,7 @@ else:
 
 G = network_loaders.loadEntireNetwork()
 
-S = nx.ego_graph(G, n, radius=3, undirected=True) 
+S = nx.ego_graph(G, n, radius=2, undirected=True) 
 
 nx.draw(
 	S,

### 2020-02-07 setup-db.sh

@@ -32,8 +32,8 @@ printf "loading missing patronage estimations...\n"
 sqlite3 "$DB_FILE" < ./queries/load-missing-patronage-estimations.sql
 rm ./temp_missing_patronages.csv
 
-printf "applying default patronage to remaining airports...\n"
-sqlite3 "$DB_FILE" < ./queries/apply-default_patronage.sql
+printf "remove those disconnected airports and their routes...\n"
+sqlite3 "$DB_FILE" < ./queries/remove_disconnected_subgraphs_without_patronage_data.sql
 
 printf "removing duplicate routes (source, destination, airline)...\n"
 sqlite3 "$DB_FILE" < ./queries/remove-duplicate-connections-by-same-airline.sql

### 2020-02-07 paper/main.tex
blablabla

@@
 example cite \cite{jirauschek20141}
+Cleaning <look at the cleaning script, shortly list what we do>
 
 \section{Data Enrichment \& Estimation}
+After cleaning up the data, there are 3139 airports.
+
+<degree distribution: even vs. odd degree occurences>
+
+Besides the main subgraph, that includes 3113 nodes, there are 6 small disconnected ones with only a couple of nodes.
+One with 10 nodes for example, consists only of airports that are located in New Caledonia, an archipelago in the Pacific Ocean. 
+<image of this example subgraph drawn on a map>
+
+In order to enable us to do more meaningful analysis, we enrich the dataset with additional information. We chose the airport patronage and found out, that we can get this data from Wikidata. 
+For 1956 of the 3139 airports from the dataset, we can find patronage data from Wikidata. 
+<describe how we do it: yearly vs. monthly + scaling from other years>
+In order to populate the remaining nodes with reasonable patronages as well, we tried different techniques. 
+First <using available data: runways -> factor -> calc. patronage per square feet + threshold, bad data quality. Show flow estimation iteration.>
+Seccond <inspired by professor: algorithm that looks at neighboring airports patronage. Describe Algorithm. Show flow estimation iteration>
+
+After estimating missing patronage data by looking at neighboring airports patronages, 14 airports without patronage remain.
+These must be in airports in disconnected subgraphs, because the algorithm would eventually reach them and assign a patronage otherwise.
+Investigations confirm that.
+We disregard these few dataless airports from disconnected subgraphs in the following analysises and thus end up with a network of 3125 airports.
+
+<Passenger flow estimation algorithm, outcomes>
 
 \section{Basic Network Analysis}
-There are 7 disconnected subgraphs in the Graph.
-Besides the main network, that includes ... nodes, there are 6 small ones with only a couple of nodes.
-One with 10 nodes for example, consists only of airports that are located in New Caledonia, an archipelago in the Pacific Ocean. 
-Another disconnected subgraph represents the connection of four airports around the San Juan Islands, an archipelago in the Pacific Northwest of the United States.
-There are two more disconnected subgraphs with four nodes and two with only two nodes.
-
-<images of these networks drawn on a map>
 
 \section{Airline Subnetwork Analysis \& Comparison}
+
+\section{Airline Cooperation Opportunity}
 
@@
 Liu \cite{airline_consolidation_and_consumer_welfare}.
-\section{Airline Cooperation Opportunity}
 

### 2020-02-07 scripts/print-subgraphs.py

@@ -10,7 +10,7 @@ connected_subgraphs = nx.connected_components(G)
 
 for i, S in enumerate(connected_subgraphs): 
 	print("Subgraph", i) 
-	print("Number of nodes:", S)
 	print(' '.join(list(S)))
+	print("Number of nodes:", len(list(S)))
 
 

### 2020-02-08 scripts/network_loaders.py
bug fix

@@ -94,6 +94,7 @@ def loadEntireNetwork(
 
 
 def loadAirlineNetwork(
+	airline_id,
 	airport_columns=default_airport_columns,
 	route_columns=default_route_columns
 	): 

### 2020-02-08 paper/main.tex
blabla

@@
 \section{Data Description}
+The network analysis is based on dataset from openflights.org. 
+It describes passenger flight connections between airports in the year 2014. 
+The data includes, which airline each connection is operated by.
+The data comes in three tables: airports, routes and airlines. 
+The airports table has entries for every airport with the following useful information: \\
+- airport id\\
+- iata and icao codes\\
+- geographic coordinates\\
+- country and region\\
 
-example cite \cite{jirauschek20141}
-Cleaning <look at the cleaning script, shortly list what we do>
+The routes table lists an entrie for each connection between two airports that was operated by an airline somewhen in the year 2014.
+It does not contain any information about flight frequencies or passenger volume.
+The airline table lists airlines associated with their name and some information we do not need like country or callsign.
+\\
+
+We are loading these files into an sqlite database for easier handling. 
+We apply some queries for cleaning the data, e.g.
+removing routes operated by unknown airlines or filling in airport ids in routes where only iata or icao code is used to refer to a source or destination airport.
+\\
+
+All the data-setup can be acomplished by running a single script.
+This script and also all other code we have written for this project can be found in a public repository \cite{repository}.
 
@@
 After cleaning up the data, there are 3139 airports. 
+Interpreting the data as a graph gives us a multiedge directed graph).
+Looking at the degree distribution in Figure~\ref{fig:degree_distribution}, the alternating characteristic of degrees strikes the eye.
+It comes from the fact, that it's very uncommon for a connection between airports to exist only in one direction.
+Thus, there is much fewer nodes with odd degrees than than with even degrees.
 
-<degree distribution: even vs. odd degree occurences>
+When we disregard odd degress, the seemingly linear distribution on a log log scale becomes apparent.
+Using least square (scipy.optimize.curve\_fit), we optimize paramters $c$ and $\gamma$ Figure~\ref{fig:degree_distribution_curves}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=76mm]{imgs/results/degree_distribution_incl_odd_degrees.png}
+	\caption{
+The degree distribution of the network on a log log scale }
+	\label{fig:degree_distribution}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=76mm]{imgs/results/degree_distribution_curve_manual.png}
+	\caption{
+Looking at even degrees only. Trying least square curve fitting to find suitable parameters for power law distribution function $f(x) = a * x^{-\gamma}$}
+	\label{fig:degree_distribution_curves}
+\end{figure}
 
 Besides the main subgraph, that includes 3113 nodes, there are 6 small disconnected ones with only a couple of nodes.
-One with 10 nodes for example, consists only of airports that are located in New Caledonia, an archipelago in the Pacific Ocean. 
-<image of this example subgraph drawn on a map>
+One with 10 nodes for example Figure~\ref{fig:new_caledonia}, consists only of airports that are located in New Caledonia, an archipelago in the Pacific Ocean. 
+\begin{figure}
+	\centering
+	\includegraphics[width=76mm]{imgs/new-caledonia-subgraph.png}
+	\caption{Airports of New Caledonia drawn on a map}
+	\label{fig:new_caledonia}
+\end{figure}
 

### 2020-02-08 setup-db.sh

@@ -1,59 +1,0 @@
-#/usr/bin/bash
-
-printf "\nusage: $0 [<db-file>]>\n"
-printf "make sure you have the following files in place:\n"
-printf "./data/{airports.dat,airlines.dat,routes.dat}\n"
-printf "./data/ourairports.com/runways.csv\n"
-printf "./airport-patronage/wikidata-airport-patronage.csv\n\n"
-
-DB_FILE=${1:-./db.db}
-
-printf "loading and cleaning openflights data...\n" 
-sqlite3 "$DB_FILE" < ./queries/load-openflights-data.sql 
-sqlite3 "$DB_FILE" < ./queries/clean-openflights-data.sql
-
-printf "exporting airport list...\n" 
-sqlite3 "$DB_FILE" < ./queries/list-airports.sql > ./airport-patronage/custom_airport_ids
-
-printf "extracting patronage from wikidata download...\n"
-pushd ./airport-patronage > /dev/null
-node ./extract-yearly-patronage.js
-node ./estimate-2014-patronage.js
-popd > /dev/null
-cp ./airport-patronage/estimated-2014-patronage.csv ./data/
-
-printf "adding patronage column...\n"
-sqlite3 "$DB_FILE" < ./queries/set-up-patronage.sql
-
-printf "estimating missing patronage...\n"
-python ./scripts/estimate-missing-patronages.py "$DB_FILE" ./temp_missing_patronages.csv
-
-printf "loading missing patronage estimations...\n"
-sqlite3 "$DB_FILE" < ./queries/load-missing-patronage-estimations.sql
-rm ./temp_missing_patronages.csv
-
-printf "remove those disconnected airports and their routes...\n"
-sqlite3 "$DB_FILE" < ./queries/remove_disconnected_subgraphs_without_patronage_data.sql
-
-printf "removing duplicate routes (source, destination, airline)...\n"
-sqlite3 "$DB_FILE" < ./queries/remove-duplicate-connections-by-same-airline.sql
-
-printf "calculating geographic distance...\n" 
-python ./scripts/calculate-geo-distance.py "$DB_FILE"
-
-printf "adding geo_distance column...\n"
-sqlite3 "$DB_FILE" < ./queries/set-up-geo-distance.sql
-rm ./temp_geo_distances.csv
-
-printf "estimating edge flows"
[…]

### 2020-02-08 scripts/degree_distribution.py
using bbox_inches='tight' for figure saving, adding log curve fitting

@@ -28,10 +28,9 @@ for degree in range(0, max_degree + 1):
 		nodes[degree] = 0
 
 pyplot.plot(degrees, nodes)
-pyplot.title('whole network degree distribution (multiple edges possible)')
 pyplot.xlabel('degree')
 pyplot.ylabel('number of nodes')
-pyplot.savefig('./results/degree_distribution.png', dpi=300)
+pyplot.savefig('./results/degree_distribution.png', dpi=300, bbox_inches='tight')
 
 pyplot.show()
 

### 2020-02-08 scripts/degree_distribution_curve_manual.py

@@ -8,51 +8,52 @@ import network_loader
 
 network = network_loader.load()
 
-degree_counts = {}
+node_counts_dict = {}
 max_degree = 0
 
 for n, d in network.degree():
 	try:
-		degree_counts[d] += 1
+		node_counts_dict[d] += 1
 	except:
-		degree_counts[d] = 1
+		node_counts_dict[d] = 1
 	if d > max_degree: 
 		max_degree = d
 
 degrees = []
-nodes = []
+node_counts = []
 
-for degree_count in degree_counts:
-	if degree_count % 2 == 0:
-		degrees.append(degree_count)
-		nodes.append(degree_counts[degree_count])
+for degree in node_counts_dict:
+	if degree % 2 == 0:
+		degrees.append(degree)
+		node_counts.append(node_counts_dict[degree])
 	
 degrees = np.array(degrees)
-nodes = np.array(nodes) 
+node_counts = np.array(node_counts) 
 
-def f1(x, c, a):
-	return c * np.power(math.e, -a * x)
+def f(x, c, a):
+	return c * np.power(x, -a)
 
-def f2(x, c, g):
-	return c * np.power(x, -g)
+def f_log(x, c, a): 
+	return np.log(f(np.exp(x), c, a))
 
-f = f2
-
-((c, a), pcov) = scipy.optimize.curve_fit(f, degrees, nodes, p0=(100,0.5))
- 
-x = np.logspace(1,np.log10(max_degree/10),100)
-y = f(x, c, a)
- 
+# manual estimation 
 mc = 4900
 ma = 1.55
-mx = x.copy()
-my = f(mx, mc, ma)
 
-plt.plot(degrees, nodes, 'o')
-plt.plot(x, y, color='red')
-plt.plot(mx, my, color='orange')
+# least square fit
+((c, a), pcov) = scipy.optimize.curve_fit(f, degrees, node_counts, p0=(100,0.5))
+ 
+# least square fit on log
+log_degrees = np.log(degrees)
+((lc, la), pcov) = scipy.optimize.curve_fit(f_log, np.log(degrees), np.log(node_counts), p0=(mc, ma)) 
 
-plt.title('whole network degree distribution (multiple edges possible, only nodes with even degrees)')
+x = np.logspace(1,np.log10(max_degree/10),100)
+
[…]

### 2020-02-08 scripts/estimate-passenger-flows.py

@@ -54,7 +54,7 @@ def run(db_file):
 	for i, airport in airports.items(): 
 		airport.recalc_flow_sum_and_deviation()
 
-	if plot_figure: 
+	if script_mode == "show": 
 		min_max_sum = plot_flow_deviation_distribution(airports)
 		labels = ["initial. min, max, sum: [{0:.2f}, {1:.2f}, {2:.2f}]".format(*min_max_sum)]
 
@@ -80,7 +80,7 @@ def run(db_file):
 		if iteration - last_plot >= plot_each: 
 			last_plot = iteration 
 			
-			if plot_figure:
+			if script_mode == "show":
 				min_max_sum = plot_flow_deviation_distribution(airports)
 				label_template = "iteration {3}. min, max, sum(abs): [{0:.2f}, {1:.2f}, {2:.2f}]"
 				labels.append(label_template.format(*min_max_sum, iteration + 1))
@@ -91,17 +91,17 @@ def run(db_file):
 
 	sys.stdout.write("\riterating 100%   \n")
 
-	if plot_figure: 
+	if script_mode == "show": 
 		pyplot.title("deviation")
 		pyplot.legend(labels, loc=2)
 		pyplot.xlabel('nodes , ordered by flow_deviation')
 		pyplot.ylabel('flow_deviation $ln(FlowSum(n)/FlowDeviation(n))$')
-
-	if script_mode == "show":
+		pyplot.savefig(
+			'./results/flow_estimation_{0}_iterations.png'.format(iterations),
+			dpi=300
+			bbox_inches='tight'
+		)
 		pyplot.show()
-
-	if save_figure: 
-		pyplot.savefig('./results/flow_estimation_{0}_iterations.png'.format(iterations), dpi=300)
 
 	if script_mode == "write_csv":
 		routes_csv = open('./temp_passenger_flows.csv', 'w')
@@ -138,24 +138,21 @@ def plot_flow_deviation_distribution(airports):
 	highest = sorted_list[-1].flow_deviation
 	return (smallest, highest, abs_integral )
 
-if len(sys.argv) > 1: 
-	script_mode = sys.argv[1]
-else:
+understood = True
+if len(sys.argv) < 2: 
 	script_mode = "show"
+else: 	
+	script_mode = sys.argv[1]
+	if script_mode not in ["show", "write_csv"]:
+		understood = False
 
-db_file = local_config.db_file
-if len(sys.argv) > 2: 
[…]

### 2020-02-08 setup-db.sh

@@ -1,0 +1,59 @@
+#/usr/bin/bash
+
+printf "\nusage: $0 [<db-file>]>\n"
+printf "make sure you have the following files in place:\n"
+printf "./data/{airports.dat,airlines.dat,routes.dat}\n"
+printf "./data/ourairports.com/runways.csv\n"
+printf "./airport-patronage/wikidata-airport-patronage.csv\n\n"
+
+DB_FILE=${1:-./db.db}
+
+printf "loading and cleaning openflights data...\n" 
+sqlite3 "$DB_FILE" < ./queries/load-openflights-data.sql 
+sqlite3 "$DB_FILE" < ./queries/clean-openflights-data.sql
+
+printf "exporting airport list...\n" 
+sqlite3 "$DB_FILE" < ./queries/list-airports.sql > ./airport-patronage/custom_airport_ids
+
+printf "extracting patronage from wikidata download...\n"
+pushd ./airport-patronage > /dev/null
+node ./extract-yearly-patronage.js
+node ./estimate-2014-patronage.js
+popd > /dev/null
+cp ./airport-patronage/estimated-2014-patronage.csv ./data/
+
+printf "adding patronage column...\n"
+sqlite3 "$DB_FILE" < ./queries/set-up-patronage.sql
+
+printf "estimating missing patronage...\n"
+python ./scripts/estimate-missing-patronages.py "$DB_FILE" ./temp_missing_patronages.csv
+
+printf "loading missing patronage estimations...\n"
+sqlite3 "$DB_FILE" < ./queries/load-missing-patronage-estimations.sql
+rm ./temp_missing_patronages.csv
+
+printf "remove those disconnected airports and their routes...\n"
+sqlite3 "$DB_FILE" < ./queries/remove_disconnected_subgraphs_without_patronage_data.sql
+
+printf "removing duplicate routes (source, destination, airline)...\n"
+sqlite3 "$DB_FILE" < ./queries/remove-duplicate-connections-by-same-airline.sql
+
+printf "calculating geographic distance...\n" 
+python ./scripts/calculate-geo-distance.py "$DB_FILE"
+
+printf "adding geo_distance column...\n"
+sqlite3 "$DB_FILE" < ./queries/set-up-geo-distance.sql
+rm ./temp_geo_distances.csv
+
+printf "estimating edge flows"
[…]

### 2020-02-09 scripts/alliances.py
calculating opportunity for staralliance

@@ -1,0 +1,10 @@
+vanilla = {
+	airline_ids: [
+		'1057',
+		'1066', 
+		'319', 
+		'1191', 
+	}
+}
+		
+

### 2020-02-09 scripts/largeness.py

@@ -12,7 +12,7 @@ def calculateForGraph(G):
 	largeness = 0
 	for i in range(n): 
 		for j in range(m): 
-			if square[i,j] > 0: #and adjm[i,j] = 0 just an idea
+			if square[i,j] > 0: #and adjm[i,j] = 0 just an idea, sai idea: i != j
 				sa_node = G.nodes[nodes[i]]
 				da_node = G.nodes[nodes[j]]
 				largeness += math.sqrt(sa_node["patronage"] * da_node["patronage"])

### 2020-02-11 scripts/alliances-opportunities.py
calculating the cooperation opportunity for 4 airline alliances

@@ -1,0 +1,41 @@
+import networkx as nx
+import sqlite3
+import matplotlib.pyplot as plt
+import sys
+
+# local modules
+from network_loaders import loadAirlineNetwork
+import largeness
+
+class Alliance:
+	def __init__(self):
+		self.airline_subgraphs = {}
+		self.largeness = 0
+		self.largeness_sum = 0
+		self.composed = None
+		pass
+
+alliances = {}
+
+for alliance_name in ['oneworld', 'skyteam', 'staralliance', 'vanilla']:
+	print(alliance_name)
+	alliance = Alliance()
+	f = open("../data/alliances/" + alliance_name)
+	for airline_id in map(lambda line: line.strip(), f): 
+		print(airline_id)
+		S = loadAirlineNetwork(airline_id)
+		alliance.airline_subgraphs[airline_id] = S
+		alliance.largeness_sum += largeness.calculateForGraph(S)
+		if alliance.composed == None:
+			alliance.composed = S
+		else: 
+			alliance.composed = nx.compose(alliance.composed, S) 
+	alliance.largeness = largeness.calculateForGraph(alliance.composed)
+
+	print('largeness sum', alliance.largeness_sum)
+	print('alliance largeness', alliance.largeness)
+	print('cooperation opportunity', alliance.largeness / alliance.largeness_sum)
+	print()
+
+	alliances[alliance_name] = alliance
+

### 2020-02-11 scripts/alliances.py

@@ -1,10 +1,0 @@
-vanilla = {
-	airline_ids: [
-		'1057',
-		'1066', 
-		'319', 
-		'1191', 
-	}
-}
-		
-

### 2020-02-11 paper/main.tex
more bla

@@
 %\usepackage{lipsum}
+\usepackage{listings}
 
@@
 All the data-setup can be acomplished by running a single script.
-This script and also all other code we have written for this project can be found in a public repository \cite{repository}.
+This script and also all other code we have written for this project can be found in a public repository on GitHub\cite{repository}.
 
@@
 When we disregard odd degress, the seemingly linear distribution on a log log scale becomes apparent.
-Using least square (scipy.optimize.curve\_fit), we optimize paramters $c$ and $\gamma$ Figure~\ref{fig:degree_distribution_curves}
+Using least square (scipy.optimize.curve\_fit), we optimize paramters $c$ and $\gamma$ as you can see in Figure~\ref{fig:degree_distribution_curves}
 
@@
 For 1956 of the 3139 airports from the dataset, we can find patronage data from Wikidata. 
-<describe how we do it: yearly vs. monthly + scaling from other years>
+We need to distinguish between monthly and yearly values and we extrapolate 2014 data from close years in case no data for the year 2014. 
 In order to populate the remaining nodes with reasonable patronages as well, we tried different techniques. 
-First <using available data: runways -> factor -> calc. patronage per square feet + threshold, bad data quality. Show flow estimation iteration.>
-Seccond <inspired by professor: algorithm that looks at neighboring airports patronage. Describe Algorithm. Show flow estimation iteration>
+First we used data about runway surfaces that we found on ourflights.org.
+We summed up the surfaces of runways for every airport and then calculated the average ratio between total runway surface area and patronage of airports where both data points were present, in order to predict patronage for airports without patronage data but with runway surface data based on this average ratio.
+For the still remaining >1000 airports without patronage we would then apply a default value that equals the avg of the smallest 1\% of airports with patronage data from Wikidata.
+The runway data turned out to be very unclean and unreliably. Water runways and other quirks were distorting the predictions.
+
+Inspired by Prof. Ikonnikova advice during the presentation we switched to estimating the remaining airport patronages by looking at neighboring airports with patronage data.
+
+\begin{lstlisting}[language=Python, caption=Patronage Estimation]
+G = loadEntireNetwork()
+pr = -1 #previous remaining
+r = 0   #remaining
+while r != pr:
+  pr = r
+  r = 0
+  ep = {} #estimated patronages
+  for apid in G.nodes:
+    node = G.nodes[apid]
+    if node["patronage"] == None:
+      neighbors = G.neighbors(apid) 
+      deg = G.degree(apid)
+      sum = 0
+      count = 0
+      for nid in neighbors: 
+        n = G.nodes[nid]
+        npatr = n["patronage"]
+        ndeg = G.degree(nid) 
+        if npatr != None: 
+          sum += deg * npatr / ndeg
+          count += 1
+      if count == 0:
+        r += 1
+      else:
+        avg = sum / count
+        ep[apid] = avg 
+  for apid in ep: 
+    node = G.nodes[apid]
+    node["patronage"] = ep[apid]
+\end{lstlisting}
+
+This seccond approach yields much nicer estimations, as we will see after estimating the flows between airports.
+
+The flows are estimated by choosing reasonable initial values and then applying corrections iteratively to approach a situation where the sum of the estimated flows for each airport equal its patronage value.
+The average initial values for an edge between airport a and b is chosen as: \footnote{hmm, vielleicht auch nicht den avg, sondern den total flow zwischen den airports so berechenen - ich mein, das hab ich ja gemacht!}
+
+$avgFlow_{ab} = $
+
+$\dfrac{patronage(a) * patronage(b)}{degree(a) * degree(b)}$
+
+Remember that we are handling a multiedge directed graph here. There may be multiple edges between two airports pointing in different directions and/or operated by different airlines.
+We could assume an equal distribution of the flows among the edges.
+But we chose trying to be closer to reality by weighting the flow of an edge between two airports $a$ and $b$, that is operated by airline $o$, by the geometric mean of the number of edges airline $o$ operates at airport $a$ and number of edges airline $o$ operates at airport $b$:
+
+$flow_{ab} = $
+
+$avgFlow_{ab} * (|E_{ab}|+|E_{ba}|) * weight_{abo}$
+
+Where $|E_{ab}|$ is the number of directed edges from $a$ to $b$ and
+
+$weight_{abo} = $
+
+$\dfrac{\sqrt{degree_{o}(a) * degree_{o}(b)}}{\displaystyle\sum_{l \in L \land c,d \in \{a,b\} \land c \neq d}(\sqrt{degree_{l}(c) * degree_{l}(d)})}$
+
+The ratios we choose here will stay intact over the course of the iterations in the next part of the algorithm.
+
+<describe iteration step>
+
+<Show results, compare runway to neighbor based estimation>
+
+The complete algorithm for passenger flow estimation is too long for beeing included in this document. You can find it in the repository: ./scripts/estimate-passenger-flows.py
 
@@
 We disregard these few dataless airports from disconnected subgraphs in the following analysises and thus end up with a network of 3125 airports.
-
-<Passenger flow estimation algorithm, outcomes>
 

### 2020-02-12 paper/main.tex
some working on formulars & trying out spell checking with aspell :)

@@
 %\usepackage{lipsum}
-\usepackage{listings}
+\usepackage{amsmath}
 
@@
 We compare airline-specific networks and find relations between their network's characteristics and their business model.
-We propose one metric that plays a role in forcasting whether a cooperation between two airlines is advantageous and use this metric to generate an alliances landscape.
-We compare it's predictive correctness to the real world by looking at the formation of Vanilla Airlines which occured in the year after the one our data stems from.
+We propose one metric that plays a role in forecasting whether a cooperation between two airlines is advantageous and use this metric to generate an alliances landscape.
+We compare it's predictive correctness to the real world by looking at the formation of Vanilla Airlines which occurred in the year after the one our data stems from.
 \end{abstract}
@@
 
-The routes table lists an entrie for each connection between two airports that was operated by an airline somewhen in the year 2014.
+The routes table lists an entry for each connection between two airports that was operated by an airline sometime in the year 2014.
 It does not contain any information about flight frequencies or passenger volume.
-The airline table lists airlines associated with their name and some information we do not need like country or callsign.
+The airline table lists airlines associated with their name and some information we do not need like country or call sign.
 \\
 
-We are loading these files into an sqlite database for easier handling. 
+We are loading these files into an SQLite database for easier handling. 
 We apply some queries for cleaning the data, e.g.
@@
 
-All the data-setup can be acomplished by running a single script.
+All the data-setup can be accomplished by running a single script.
 This script and also all other code we have written for this project can be found in a public repository on GitHub\cite{repository}.
@@
 After cleaning up the data, there are 3139 airports. 
-Interpreting the data as a graph gives us a multiedge directed graph).
+Interpreting the data as a graph gives us a multi-edge directed graph).
 Looking at the degree distribution in Figure~\ref{fig:degree_distribution}, the alternating characteristic of degrees strikes the eye.
@@
 
-When we disregard odd degress, the seemingly linear distribution on a log log scale becomes apparent.
-Using least square (scipy.optimize.curve\_fit), we optimize paramters $c$ and $\gamma$ as you can see in Figure~\ref{fig:degree_distribution_curves}
+When we disregard odd degrees, the seemingly linear distribution on a log log scale becomes apparent.
+Using least square (scipy.optimize.curve\_fit), we optimize parameters $c$ and $\gamma$ as you can see in Figure~\ref{fig:degree_distribution_curves}
 
@@
 
-This seccond approach yields much nicer estimations, as we will see after estimating the flows between airports.
+This second approach yields much nicer estimations, as we will see after estimating the flows between airports.
 
 The flows are estimated by choosing reasonable initial values and then applying corrections iteratively to approach a situation where the sum of the estimated flows for each airport equal its patronage value.
-The average initial values for an edge between airport a and b is chosen as: \footnote{hmm, vielleicht auch nicht den avg, sondern den total flow zwischen den airports so berechenen - ich mein, das hab ich ja gemacht!}
+The average initial values for an edge between airport $p$ and $q$ is chosen as:
 
-$avgFlow_{ab} = $
+\begin{equation}
+avgFlow(pq) = \dfrac{patronage(p) * patronage(q)}{degree(p) * degree(q)}
+\end{equation}
 
-$\dfrac{patronage(a) * patronage(b)}{degree(a) * degree(b)}$
+Remember that we are handling a multi-edge directed graph here.
 
-Remember that we are handling a multiedge directed graph here. There may be multiple edges between two airports pointing in different directions and/or operated by different airlines.
+\begin{equation}
+E = \{(pql) | \exists\ \text{route from}\ p\ \text{to}\ q\ \text{by}\ l\}
+\end{equation}
+
+where $p$ and $q$ are airports and $l$ is an airline.
+Let us introduce a function $E(pq)$ that returns all edges between $p$ and $q$ disregarding the direction and operating airline. 
+\begin{equation}
+E(pq) = \{pql | \exists_{l \in L}:pql \in E \lor qpl \in E\}
+\end{equation}
+
+where $L$ is the set of airlines.
+
+And let us introduce the function $E(p)$ that returns all edges from and to an airport $p$ by every airline: 
+\begin{equation}
+E(p) = \{rsl | (r=p \lor s=p) \land \exists_{l \in L}:rsl \in E \}
+\end{equation}
+
+The Edges of the graph are thus triplets of a source airport, destination airport and an airline.
+There may be multiple edges between two airports pointing in different directions and/or operated by different airlines.
 We could assume an equal distribution of the flows among the edges.
-But we chose trying to be closer to reality by weighting the flow of an edge between two airports $a$ and $b$, that is operated by airline $o$, by the geometric mean of the number of edges airline $o$ operates at airport $a$ and number of edges airline $o$ operates at airport $b$:
+But we chose trying to be closer to reality by weighting the flow of an edge between two airports $p$ and $q$, that is operated by airline $l$, by the geometric mean of the number of edges airline $l$ operates at airport $p$ and number of edges airline $l$ operates at airport $q$:
 
-$flow_{ab} = $
+\begin{equation}
+\begin{aligned}
+&flow(pql) =\\
+={}&avgFlow(pq)  
+* noe(pq) 
+* weight(pql) 
+\end{aligned}
+\end{equation}
 
-$avgFlow_{ab} * (|E_{ab}|+|E_{ba}|) * weight_{abo}$
+where $noe(pq)$ is the number of edges between airport $p$ and $q$ and $weight(pql)$ is defined as follows:
 
-Where $|E_{ab}|$ is the number of directed edges from $a$ to $b$ and
+\begin{equation}
+\begin{aligned}
+&weight(pql) = \dfrac{\sqrt{degree_{l}(p) * degree_{l}(q)}}{pnws(pql)}
+\end{aligned}
+\end{equation}
 
-$weight_{abo} = $
+where the $pnws(pq)$ (Pre Normalization Weight Sum) is just the sum of the non-normalized weights of all the routes from different airlines to normalize the weights.
 
-$\dfrac{\sqrt{degree_{o}(a) * degree_{o}(b)}}{\displaystyle\sum_{l \in L \land c,d \in \{a,b\} \land c \neq d}(\sqrt{degree_{l}(c) * degree_{l}(d)})}$
+\begin{equation}
+\begin{aligned}
+&pnws(pq) = \\
+={}&\displaystyle\sum_{rsm \in E(pq)}(\sqrt{degree_{m}(r) * degree_{m}(s)})
+\end{aligned}
+\end{equation}
+
+where $degree_l(p)$ is the degree of airport $p$ in airline $l$'s subgraph, i.e. number of edges from and to airport $p$ operated by airline $l$.
 
 The ratios we choose here will stay intact over the course of the iterations in the next part of the algorithm. 
+In every iteration, we traverse all airports and for every airport we calculate the sum of current flows values of all routes.
+
+\begin{equation}
+\begin{aligned}
+flowSum(p) = \displaystyle\sum_{pql \in E \cup pu \in E}flow_{pql}
+\end{aligned}
+\end{equation}
+
+Difference between the patronage and the current sum of passenger flows of incoming and outgoing routes. 
+Then, for each airport we calculate
+
+\begin{equation}
+\begin{aligned}
+& flow_{pql}' = flow_{abo} \\
+& \displaystyle\sum_{a \in A | ab \in E \lor ba \in E} 
+\end{aligned}
+\end{equation}
 
@@
 
-The complete algorithm for passenger flow estimation is too long for beeing included in this document. You can find it in the repository: ./scripts/estimate-passenger-flows.py
+The complete algorithm for passenger flow estimation is too long for being included in this document. You can find it in the repository: ./scripts/estimate-passenger-flows.py
 
@@
 Investigations confirm that.
-We disregard these few dataless airports from disconnected subgraphs in the following analysises and thus end up with a network of 3125 airports.
+We disregard these few dataless airports from disconnected subgraphs in the following analyses and thus end up with a network of 3125 airports.
 
@@
 
-\section{Airline Subnetwork Analysis \& Comparison}
+\section{Airline Subgraph Analysis \& Comparison}
 
@@
 
-The possibility to provide convenient on-line connections to clients is an important factor that drives welfare gains through ailine cooperation according to E.
+The possibility to provide convenient on-line connections to clients is an important factor that drives welfare gains through airline cooperation according to E.
 E.
@@
 
-\section*{Acknowledgements}
+\section*{Acknowledgments}
 

### 2020-02-12 paper/main.tex
describing the iteration of flow estimation

@@
 
+After estimating missing patronage data by looking at neighboring airports patronages, 14 airports without patronage remain.
+These must be in airports in disconnected subgraphs, because the algorithm would eventually reach them and assign a patronage otherwise.
+Investigations confirm that.
+We disregard these few dataless airports from disconnected subgraphs in the following analyses and thus end up with a network of 3125 airports.
+
 The flows are estimated by choosing reasonable initial values and then applying corrections iteratively to approach a situation where the sum of the estimated flows for each airport equal its patronage value.
 The average initial values for an edge between airport $p$ and $q$ is chosen as: 
-
 \begin{equation}
@@
 \end{equation}
-
 Remember that we are handling a multi-edge directed graph here. 
-
 \begin{equation}
@@
 \end{equation}
-
 where $p$ and $q$ are airports and $l$ is an airline.
@@
 \end{equation}
-
 where $L$ is the set of airlines.
@@
 \end{equation}
-
 The Edges of the graph are thus triplets of a source airport, destination airport and an airline.
@@
 But we chose trying to be closer to reality by weighting the flow of an edge between two airports $p$ and $q$, that is operated by airline $l$, by the geometric mean of the number of edges airline $l$ operates at airport $p$ and number of edges airline $l$ operates at airport $q$:
-
 \begin{equation}
@@
 \end{equation}
-
 where $noe(pq)$ is the number of edges between airport $p$ and $q$ and $weight(pql)$ is defined as follows: 
-
 \begin{equation}
@@
 \end{equation}
-
 where the $pnws(pq)$ (Pre Normalization Weight Sum) is just the sum of the non-normalized weights of all the routes from different airlines to normalize the weights. 
-
 \begin{equation}
@@
 \end{equation}
-
 where $degree_l(p)$ is the degree of airport $p$ in airline $l$'s subgraph, i.e. number of edges from and to airport $p$ operated by airline $l$.
@@
 In every iteration, we traverse all airports and for every airport we calculate the sum of current flows values of all routes. 
-
 \begin{equation}
@@
 \end{equation}
-
 Difference between the patronage and the current sum of passenger flows of incoming and outgoing routes. 
-Then, for each airport we calculate
-
+Then, for each airport we calculate the difference between its patronage and the current sum of flows.
 \begin{equation}
 \begin{aligned}
-& flow_{pql}' = flow_{abo} \\
-& \displaystyle\sum_{a \in A | ab \in E \lor ba \in E} 
+flowDiff(p) = patronage(p) - flowSum(p) 
+\end{aligned}
+\end{equation}
+With this information given, we can now calculate for every edge $pql$ the change in its flow. 
+\begin{equation}
+\begin{aligned}
+\forall_{pql \in E(p)}: & \\
+& \Delta flow(pql) = & \\ 
+& ={} \dfrac{flow(pql)}{flowSum(p)}flowDiff(p) \\
+& +{} \dfrac{flow(pql)}{flowSum(q)}flowDiff(q) \\
+\end{aligned}
+\end{equation}
+and the more perfect flows for the edges and starting point for the next itaration are
+\begin{equation}
+\begin{aligned}
+\forall_{pql \in E(p)}: & \\
+& flow'(pql) = flow_{abo} + \Delta flow(pql)
 \end{aligned}
@@
 
-<describe iteration step>
+In order to look at the results of this algorithm we introduce a measure 
+\begin{equation}
+flowDeviation(p) = ln(flowSum(p)/patronage(p))
+\end{equation}
+it expresses how well the sum of estimated flows match the patronage, that we know for the airport.
+If the flows are half the patronage the absolute value of $flowDeviation$ will be the same as when the current flows are twice the actual patronage number.
+We compare the results between estimating the patronages based on the runway sizes Figure~\ref{fig:flow_deviation_runway} and estimating the patronages based on neighboring airports Figure~\ref{fig:flow_deviation}.
+The blue line shows the $flowDeviation$ distribution of the initial flow values.
+The other almost totally overlapping lines show the $flowDeviation$ distribution after a couple of iterations.
 
-<Show results, compare runway to neighbor based estimation>
+The bad results of the estimations when estimating patronage values from runways stem from constellations like in Figure~\ref{fig:impossible_flows}, when choosing flows to match the patronage values are impossible.
 
-The complete algorithm for passenger flow estimation is too long for being included in this document. You can find it in the repository: ./scripts/estimate-passenger-flows.py
+\begin{figure}
+	\centering
+	\includegraphics[width=76mm]{imgs/flow_estimation_runway_approach_deviation.png}
+	\caption{
+Estimated flows when estimating patronage based on the runway size }
+	\label{fig:flow_deviation_runway}
+\end{figure}
 
-After estimating missing patronage data by looking at neighboring airports patronages, 14 airports without patronage remain.
-These must be in airports in disconnected subgraphs, because the algorithm would eventually reach them and assign a patronage otherwise.
-Investigations confirm that.
-We disregard these few dataless airports from disconnected subgraphs in the following analyses and thus end up with a network of 3125 airports.
+\begin{figure}
+	\centering
+	\includegraphics[width=76mm]{imgs/results/flow_estimation_120_iterations.png}
+	\caption{
+Estimated flows when estimating patronage based on neighboring airport's patronage}
+	\label{fig:flow_deviation}
+\end{figure}
+
+The complete algorithm for passenger flow estimation can be found in the repository: ./scripts/estimate-passenger-flows.py
 

### 2020-02-12 scripts/degree_distribution_curve_manual.py
small changes

@@ -34,7 +34,7 @@ def f(x, c, a):
 	return c * np.power(x, -a)
 
 def f_log(x, c, a): 
-	return np.log(f(np.exp(x), c, a))
+	return f(np.exp(x), c, a)
 
 # manual estimation 
 mc = 4900
@@ -45,7 +45,7 @@ ma = 1.55
  
 # least square fit on log
 log_degrees = np.log(degrees)
-((lc, la), pcov) = scipy.optimize.curve_fit(f_log, np.log(degrees), np.log(node_counts), p0=(mc, ma)) 
+((lc, la), pcov) = scipy.optimize.curve_fit(f_log, degrees, np.log(node_counts), p0=(mc, ma)) 
 
 x = np.logspace(1,np.log10(max_degree/10),100)
 

### 2020-02-12 scripts/estimate-passenger-flows.py

@@ -59,7 +59,7 @@ def run(db_file):
 		labels = ["initial. min, max, sum: [{0:.2f}, {1:.2f}, {2:.2f}]".format(*min_max_sum)]
 
 	iterations = 120
-	plot_each = iterations / 12
+	plot_each = iterations / 4
 	last_plot = -1
 	factor = math.pow(0.9, 1 / iterations) 
 	p = 0
@@ -92,13 +92,12 @@ def run(db_file):
 	sys.stdout.write("\riterating 100%   \n")
 
 	if script_mode == "show": 
-		pyplot.title("deviation")
 		pyplot.legend(labels, loc=2)
-		pyplot.xlabel('nodes , ordered by flow_deviation')
-		pyplot.ylabel('flow_deviation $ln(FlowSum(n)/FlowDeviation(n))$')
+		pyplot.xlabel('airports, ordered by flowDeviation')
+		pyplot.ylabel('flowDeviation')
 		pyplot.savefig(
 			'./results/flow_estimation_{0}_iterations.png'.format(iterations),
-			dpi=300
+			dpi=300,
 			bbox_inches='tight'
 		)
 		pyplot.show()

### 2020-02-12 scripts/estimate-passenger-flows.py
making the graphs nice

@@ -59,7 +59,7 @@ def run(db_file):
 		labels = ["initial. min, max, sum: [{0:.2f}, {1:.2f}, {2:.2f}]".format(*min_max_sum)]
 
 	iterations = 120
-	plot_each = iterations / 12
+	plot_num = 5
 	last_plot = -1
 	factor = math.pow(0.9, 1 / iterations) 
 	p = 0
@@ -77,8 +77,7 @@ def run(db_file):
 		for i, airport in airports.items():
 			airport.recalc_flow_sum_and_deviation()
 		
-		if iteration - last_plot >= plot_each: 
-			last_plot = iteration 
+		if iteration < plot_num or iteration == iterations - 1: 
 			
 			if plot_figure:
 				min_max_sum = plot_flow_deviation_distribution(airports)
@@ -92,16 +91,13 @@ def run(db_file):
 	sys.stdout.write("\riterating 100%   \n")
 
 	if plot_figure: 
-		pyplot.title("deviation")
 		pyplot.legend(labels, loc=2)
-		pyplot.xlabel('nodes , ordered by flow_deviation')
-		pyplot.ylabel('flow_deviation $ln(FlowSum(n)/FlowDeviation(n))$')
+		pyplot.xlabel('nodes, ordered by flowDeviation')
+		pyplot.ylabel('flowDeviation $ln(FlowSum(n)/FlowDeviation(n))$')
+		pyplot.savefig('./results/flow_estimation_{0}_iterations.png'.format(iterations), dpi=300, bbox_inches='tight')
 
 	if script_mode == "show":
 		pyplot.show()
-
-	if save_figure: 
-		pyplot.savefig('./results/flow_estimation_{0}_iterations.png'.format(iterations), dpi=300)
 
 	if script_mode == "write_csv":
 		routes_csv = open('./temp_passenger_flows.csv', 'w')
@@ -149,7 +145,8 @@ if len(sys.argv) > 2:
 	save_figure = sys.argv[2] == "save_figure"
 	if save_figure:
 		db_file_i += 1
-	db_file = sys.argv[db_file_i]
+	if len(sys.argv) > 3: 
+		db_file = sys.argv[db_file_i]
 else:
 	save_figure = False
 

### 2020-02-12 scripts/show-ego-net.py

@@ -22,4 +22,6 @@ nx.draw(
 	node_color=['#993322' if n == k else '#4477ee' for k in S.nodes],
 	node_size=100
 )
+plt.savefig('./results/ego_graph_{0}.png'.format(n))
 plt.show()
+

### 2020-02-12 paper/main.tex
flow estimation results

@@
 
+\begin{figure}
+	\centering
+	\includegraphics[width=76mm]{imgs/runway-based-estimation-problem.png}
+	\caption{
+For Qaanaaq Airport there was no patronage data from Wikidata and no runway information.
+That's why it ended up with the default patronage value 1523.
+In this constallation it is impossible to choose passenger flows that even remotely satisfy the the patronages of airports with ids 10, 5446, 5448}
+	\label{fig:impossible_flows}
+\end{figure}
+
 \section{Basic Network Analysis}

### 2020-02-12 scripts/estimate-passenger-flows.py

@@ -59,8 +59,7 @@ def run(db_file):
 		labels = ["initial. min, max, sum: [{0:.2f}, {1:.2f}, {2:.2f}]".format(*min_max_sum)]
 
 	iterations = 120
-	plot_each = iterations / 4
-	last_plot = -1
+	plot_times = 5
 	factor = math.pow(0.9, 1 / iterations) 
 	p = 0
 	for iteration in range(0, iterations):
@@ -77,8 +76,7 @@ def run(db_file):
 		for i, airport in airports.items():
 			airport.recalc_flow_sum_and_deviation()
 		
-		if iteration - last_plot >= plot_each: 
-			last_plot = iteration 
+		if iteration < plot_times or iteration == iterations - 1: 
 			
 			if script_mode == "show":
 				min_max_sum = plot_flow_deviation_distribution(airports)
@@ -92,6 +90,8 @@ def run(db_file):
 	sys.stdout.write("\riterating 100%   \n")
 
 	if script_mode == "show": 
+		axes = pyplot.gca()
+		axes.set_ylim([-2,4])
 		pyplot.legend(labels, loc=2)
 		pyplot.xlabel('airports, ordered by flowDeviation')
 		pyplot.ylabel('flowDeviation')

### 2020-02-12 paper/main.tex
comparing the patronage estimation based on runway size and a default value to patronage estimation based on neighboring airport's patronage by looking at the flowDeviation distribution and the worst constellation in each cases

--- 2020-02-12 paper/main.tex
@@
 \date{Received: 19.02.2020 - This is work in progress}
+
+% for the equation stuff 
+\DeclareMathOperator{\avgFlow}{avgFlow}
+\DeclareMathOperator{\patronage}{patronage}
+\DeclareMathOperator{\flow}{flow}
+\DeclareMathOperator{\weight}{weight}
+\DeclareMathOperator{\PNWS}{PNWS}
+\DeclareMathOperator{\NOE}{NOE}
+\DeclareMathOperator{\degree}{degree}
+\DeclareMathOperator{\flowSum}{flowSum}
+\DeclareMathOperator{\flowDeviation}{flowDeviation}
+\DeclareMathOperator{\flowDiff}{flowDiff}
 
@@
 For 1956 of the 3139 airports from the dataset, we can find patronage data from Wikidata.
+Get an impression about the regional differences of data availability by looking at the percentage of airports for which Wikidata yields a patronage in Table~\ref{tab:patr_av_most_airports} and Table~\ref{tab:patr_av_worst}.
+\begin{table}[h]
+	\centering
+	\caption{patronage data availability on Wikidata for countries with the most airports}
+	\label{tab:patr_av_most_airports}
+	\begin{tabular}{|l|c|c|}
+		\hline
+		Country & Airports & patronage present \\ \hline
+		United States & 539 & 34.1\%\\
+		China & 173 & 95.4\%\\
+		Canada & 142 & 48.6\%\\
+		Brazil & 122 & 93.4\%\\
+		Australia & 113 & 77.0\%\\
+		Russia & 103 & 96.1\%\\
+		India & 70 & 92.9\%\\
+		Indonesia & 63 & 60.3\%\\
+		Japan & 62 & 82.3\%\\
+		Mexico & 56 & 92.9\%\\
+		France & 55 & 96.4\%\\ \hline
+	\end{tabular}
+\end{table}
+\begin{table}[h]
+	\centering
+	\caption{patronage data availability - worst countries}
+	\label{tab:patr_av_worst}
+	\begin{tabular}{|l|c|c|}
+		\hline
+		Country & Airports & patronage present \\ \hline
+		Venezuela & 23 & 4.3\%\\
+		Bahamas & 17 & 5.9\%\\
+		Chile & 16 & 6.3\%\\
+		Ecuador & 14 & 7.1\%\\
+		Ethiopia & 13 & 7.7\%\\ 
+		Mozambique & 10 & 10.0\%\\
+		Cuba & 9 & 11.1\%\\
+		Kenya & 16 & 12.5\%\\
+		Namibia & 8 & 12.5\%\\
+		Madagascar & 13 & 15.4\%\\
+		Algeria & 26 & 19.2\%\\ \hline
+	\end{tabular}
+\end{table}
 We need to distinguish between monthly and yearly values and we extrapolate 2014 data from close years in case no data for the year 2014. 
@@
 First we used data about runway surfaces that we found on ourflights.org.
+
 We summed up the surfaces of runways for every airport and then calculated the average ratio between total runway surface area and patronage of airports where both data points were present, in order to predict patronage for airports without patronage data but with runway surface data based on this average ratio.
-For the still remaining >1000 airports without patronage we would then apply a default value that equals the avg of the smallest 1\% of airports with patronage data from Wikidata.
+For the still remaining >1000 airports without patronage we would then apply a default value that equals the average of the smallest 1\% of airports with patronage data from Wikidata.
 The runway data turned out to be very unclean and unreliably. Water runways and other quirks were distorting the predictions.
 
-Inspired by Prof. Ikonnikova advice during the presentation we switched to estimating the remaining airport patronages by looking at neighboring airports with patronage data.
-
-\begin{lstlisting}[language=Python, caption=Patronage Estimation]
+Inspired by Prof.
+Ikonnikova advice during the presentation we switched to estimating the remaining airport patronages by looking at neighboring airports with patronage data.
+The Algorithm can be seen in Listing~\ref{lst:patronage_estimation_algorithm}.
+\begin{lstlisting}[language=Python, caption={Patronage estimation algorithm, that using neighboring airport's patronage data}, label=lst:patronage_estimation_algorithm]
 G = loadEntireNetwork()
@@
 \end{lstlisting}
-
 This second approach yields much nicer estimations, as we will see after estimating the flows between airports.
@@
 The average initial values for an edge between airport $p$ and $q$ is chosen as:
+
 \begin{equation}
-avgFlow(pq) = \dfrac{patronage(p) * patronage(q)}{degree(p) * degree(q)}
+\avgFlow(pq) = \dfrac{\patronage(p) * \patronage(q)}{\degree(p) * \degree(q)}
 \end{equation}
@@
 \begin{aligned}
-&flow(pql) =\\
-={}&avgFlow(pq)  
-* noe(pq) 
-* weight(pql) 
+&\flow(pql) =\\
+={}&\avgFlow(pq)  
+* \NOE(pq) 
+* \weight(pql) 
 \end{aligned}
 \end{equation}
-where $noe(pq)$ is the number of edges between airport $p$ and $q$ and $weight(pql)$ is defined as follows: 
+where $\NOE(pq)$ is the number of edges between airport $p$ and $q$ and $\weight(pql)$ is defined as follows: 
 \begin{equation}
 \begin{aligned}
-&weight(pql) = \dfrac{\sqrt{degree_{l}(p) * degree_{l}(q)}}{pnws(pql)}
+&\weight(pql) = \dfrac{\sqrt{\degree_{l}(p) * \degree_{l}(q)}}{\PNWS(pql)}
 \end{aligned}
 \end{equation}
-where the $pnws(pq)$ (Pre Normalization Weight Sum) is just the sum of the non-normalized weights of all the routes from different airlines to normalize the weights. 
+where the $\PNWS(pq)$ (Pre Normalization Weight Sum) is just the sum of the non-normalized weights of all the routes from different airlines used to normalize the weights. 
 \begin{equation}
 \begin{aligned}
-&pnws(pq) = \\
-={}&\displaystyle\sum_{rsm \in E(pq)}(\sqrt{degree_{m}(r) * degree_{m}(s)})
+&\PNWS(pq) = \\
+={}&\displaystyle\sum_{rsm \in E(pq)}(\sqrt{\degree_{m}(r) * \degree_{m}(s)})
 \end{aligned}
 \end{equation}
-where $degree_l(p)$ is the degree of airport $p$ in airline $l$'s subgraph, i.e. number of edges from and to airport $p$ operated by airline $l$.
+where $\degree_l(p)$ is the degree of airport $p$ in airline $l$'s subgraph, i.e. number of edges from and to airport $p$ operated by airline $l$.
 
@@
 \begin{aligned}
-flowSum(p) = \displaystyle\sum_{pql \in E \cup pu \in E}flow_{pql}
+\flowSum(p) = \displaystyle\sum_{pql \in E \cup pu \in E}\flow_{pql}
 \end{aligned}
@@
 \begin{aligned}
-flowDiff(p) = patronage(p) - flowSum(p) 
+\flowDiff(p) = \patronage(p) - \flowSum(p) 
 \end{aligned}
@@
 \forall_{pql \in E(p)}: & \\
-& \Delta flow(pql) = & \\ 
-& ={} \dfrac{flow(pql)}{flowSum(p)}flowDiff(p) \\
-& +{} \dfrac{flow(pql)}{flowSum(q)}flowDiff(q) \\
+& \Delta \flow(pql) = & \\ 
+& ={} \dfrac{\flow(pql)}{\flowSum(p)}\flowDiff(p) \\
+& +{} \dfrac{\flow(pql)}{\flowSum(q)}\flowDiff(q) \\
 \end{aligned}
@@
 \forall_{pql \in E(p)}: & \\
-& flow'(pql) = flow_{abo} + \Delta flow(pql)
+& \flow'(pql) = \flow_{abo} + \Delta \flow(pql)
 \end{aligned}
@@
 \begin{equation}
-flowDeviation(p) = ln(flowSum(p)/patronage(p))
+\flowDeviation(p) = ln\left(\dfrac{\flowSum(p)}{\patronage(p)}\right)
 \end{equation}
 it expresses how well the sum of estimated flows match the patronage, that we know for the airport.
-If the flows are half the patronage the absolute value of $flowDeviation$ will be the same as when the current flows are twice the actual patronage number.
+If the flows are half the patronage the absolute value of $\flowDeviation$ will be the same as when the current flows are twice the actual patronage number.
 We compare the results between estimating the patronages based on the runway sizes Figure~\ref{fig:flow_deviation_runway} and estimating the patronages based on neighboring airports Figure~\ref{fig:flow_deviation}.
-The blue line shows the $flowDeviation$ distribution of the initial flow values.
-The other almost totally overlapping lines show the $flowDeviation$ distribution after a couple of iterations.
+The blue line shows the $\flowDeviation$ distribution of the initial flow values.
+The other lines show the $\flowDeviation$ distribution after a the first couple of iterations and after the final iteration. 
+In the case of patronage estimations based on neighboring airports, we see that the $\flowDeviation$ distribution after the 120th iteration comes very close to $y=0$ which is also reflected by the $sum(abs)$ in the legend which is the sum of the absolute value of $\flowDeviation$ over all airports which is $0.94$ in this case.
 
 The bad results of the estimations when estimating patronage values from runways stem from constellations like in Figure~\ref{fig:impossible_flows}, when choosing flows to match the patronage values are impossible.
+The constellation that accounts for $>0.88$ of the $\flowDeviation$ sum $0.94$ in the scenario where patronages are estimated based on neighboring airports is shown in Figure~\ref{fig:worst_flow_fit}.
+The patronage of both airports comes from Wikidata.
+After further investigation it turns out to be probable, that there should be a connection between Arvidsjaur Airport and Stockholm-Arlanda Airport, which is not present in the data set.
 
-\begin{figure}
+\begin{figure}[h]
 	\centering
@@
 	\caption{
-Estimated flows when estimating patronage based on the runway size }
+Estimated flows when estimating patronage based on the runway size and a default value}
 	\label{fig:flow_deviation_runway}
@@
 
-\begin{figure}
+\begin{figure}[h]
 	\centering
@@
 
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=76mm]{imgs/runway-based-estimation-problem.png}
+	\caption{Worst situation in the scenario, where patronages are estimated based on runways and a default value: 
+For Qaanaaq Airport there was no patronage data from Wikidata and no runway information.
+That's why it ended up with the default patronage value 1523.
+In this constallation it is impossible to choose passenger flows that even remotely satisfy the the patronages of airports with ids 10 and 5446}
+	\label{fig:impossible_flows}
+\end{figure}
+
+\begin{figure}[h]
+
+	\centering
+	\includegraphics[width=76mm]{imgs/results/ego_graph_730.png}
+	\caption{Worst situation in the scenario, where patronage is based on neighboring airport's patronage: 
+Arvidsjaur Airport is only connected to Lycksele Airport but has a more than twice as high patronage than Lycksele Airport}
+	\label{fig:worst_flow_fit}
+\end{figure}
 \section{Basic Network Analysis}

### 2020-02-12 setup-db.sh

@@ -56,4 +56,3 @@ rm ./temp_flow_estimation_metrics.csv
 
 printf "\ndone, enjoy.\n\n" 
 
-

### 2020-02-12 scripts/show-ego-net.py
manual padding

@@ -14,7 +14,9 @@ else:
 
 G = network_loaders.loadEntireNetwork()
 
-S = nx.ego_graph(G, n, radius=3, undirected=True) 
+S = nx.ego_graph(G, n, radius=2, undirected=True) 
+
+
 
 nx.draw(
 	S,
@@ -22,6 +24,9 @@ nx.draw(
 	node_color=['#993322' if n == k else '#4477ee' for k in S.nodes],
 	node_size=100
 )
-plt.savefig('./results/ego_graph_{0}.png'.format(n))
-plt.show()
 
+plt.xlim(-1.5,1.5)
+plt.ylim(-1.5,1.5)
+
+plt.savefig('results/ego_graph_{0}.png'.format(n), pad_inches=0.5, dpi=300)
+plt.show()

### 2020-02-15 paper/main.tex
small change
network analysis

--- 2020-02-12 paper/main.tex
@@
 %\usepackage{lipsum}
-\usepackage{amsmath}
+\usepackage{listings}
 
@@
 We compare airline-specific networks and find relations between their network's characteristics and their business model.
-We propose one metric that plays a role in forecasting whether a cooperation between two airlines is advantageous and use this metric to generate an alliances landscape.
-We compare it's predictive correctness to the real world by looking at the formation of Vanilla Airlines which occurred in the year after the one our data stems from.
+We propose one metric that plays a role in forcasting whether a cooperation between two airlines is advantageous and use this metric to generate an alliances landscape.
+We compare it's predictive correctness to the real world by looking at the formation of Vanilla Airlines which occured in the year after the one our data stems from.
 \end{abstract}
@@
 
-The routes table lists an entry for each connection between two airports that was operated by an airline sometime in the year 2014.
+The routes table lists an entrie for each connection between two airports that was operated by an airline somewhen in the year 2014.
 It does not contain any information about flight frequencies or passenger volume.
-The airline table lists airlines associated with their name and some information we do not need like country or call sign.
+The airline table lists airlines associated with their name and some information we do not need like country or callsign.
 \\
 
-We are loading these files into an SQLite database for easier handling. 
+We are loading these files into an sqlite database for easier handling. 
 We apply some queries for cleaning the data, e.g.
@@
 
-All the data-setup can be accomplished by running a single script.
+All the data-setup can be acomplished by running a single script.
 This script and also all other code we have written for this project can be found in a public repository on GitHub\cite{repository}.
@@
 After cleaning up the data, there are 3139 airports. 
-Interpreting the data as a graph gives us a multi-edge directed graph).
+Interpreting the data as a graph gives us a multiedge directed graph).
 Looking at the degree distribution in Figure~\ref{fig:degree_distribution}, the alternating characteristic of degrees strikes the eye.
@@
 
-When we disregard odd degrees, the seemingly linear distribution on a log log scale becomes apparent.
-Using least square (scipy.optimize.curve\_fit), we optimize parameters $c$ and $\gamma$ as you can see in Figure~\ref{fig:degree_distribution_curves}
+When we disregard odd degress, the seemingly linear distribution on a log log scale becomes apparent.
+Using least square (scipy.optimize.curve\_fit), we optimize paramters $c$ and $\gamma$ as you can see in Figure~\ref{fig:degree_distribution_curves}
 
@@
 
-This second approach yields much nicer estimations, as we will see after estimating the flows between airports.
+This seccond approach yields much nicer estimations, as we will see after estimating the flows between airports.
+
+The flows are estimated by choosing reasonable initial values and then applying corrections iteratively to approach a situation where the sum of the estimated flows for each airport equal its patronage value.
+The average initial values for an edge between airport a and b is chosen as: \footnote{hmm, vielleicht auch nicht den avg, sondern den total flow zwischen den airports so berechenen - ich mein, das hab ich ja gemacht!}
+
+$avgFlow_{ab} = $
+
+$\dfrac{patronage(a) * patronage(b)}{degree(a) * degree(b)}$
+
+Remember that we are handling a multiedge directed graph here. There may be multiple edges between two airports pointing in different directions and/or operated by different airlines.
+We could assume an equal distribution of the flows among the edges.
+But we chose trying to be closer to reality by weighting the flow of an edge between two airports $a$ and $b$, that is operated by airline $o$, by the geometric mean of the number of edges airline $o$ operates at airport $a$ and number of edges airline $o$ operates at airport $b$:
+
+$flow_{ab} = $
+
+$avgFlow_{ab} * (|E_{ab}|+|E_{ba}|) * weight_{abo}$
+
+Where $|E_{ab}|$ is the number of directed edges from $a$ to $b$ and
+
+$weight_{abo} = $
+
+$\dfrac{\sqrt{degree_{o}(a) * degree_{o}(b)}}{\displaystyle\sum_{l \in L \land c,d \in \{a,b\} \land c \neq d}(\sqrt{degree_{l}(c) * degree_{l}(d)})}$
+
+The ratios we choose here will stay intact over the course of the iterations in the next part of the algorithm.
+
+<describe iteration step>
+
+<Show results, compare runway to neighbor based estimation>
+
+The complete algorithm for passenger flow estimation is too long for beeing included in this document. You can find it in the repository: ./scripts/estimate-passenger-flows.py
 
@@
 Investigations confirm that.
-We disregard these few dataless airports from disconnected subgraphs in the following analyses and thus end up with a network of 3125 airports.
+We disregard these few dataless airports from disconnected subgraphs in the following analysises and thus end up with a network of 3125 airports.
 
-The flows are estimated by choosing reasonable initial values and then applying corrections iteratively to approach a situation where the sum of the estimated flows for each airport equal its patronage value.
-The average initial values for an edge between airport $p$ and $q$ is chosen as: 
-\begin{equation}
-avgFlow(pq) = \dfrac{patronage(p) * patronage(q)}{degree(p) * degree(q)}
-\end{equation}
-Remember that we are handling a multi-edge directed graph here. 
-\begin{equation}
-E = \{(pql) | \exists\ \text{route from}\ p\ \text{to}\ q\ \text{by}\ l\}
-\end{equation}
-where $p$ and $q$ are airports and $l$ is an airline.
-Let us introduce a function $E(pq)$ that returns all edges between $p$ and $q$ disregarding the direction and operating airline. 
-\begin{equation}
-E(pq) = \{pql | \exists_{l \in L}:pql \in E \lor qpl \in E\}
-\end{equation}
-where $L$ is the set of airlines.
+\section{Basic Network Analysis}
+Initially, we would like to analyse the entire worldwide airline network, and provide some insights regarding the airline industry.
+Since a particular route could be provided by multiple Airline Companies, the final network that we come up with is a Multiple Directed Network.
+The attributes of each edge in this network included both the geometrical distance and the average passenger flow of that route (edge). 
+As we can see from the Table~\ref{Tab:distance_metrics}, the diameter of the entire network is given along with the Total Distance of the routes and the Average Distance of routes in a network.
 
-And let us introduce the function $E(p)$ that returns all edges from and to an airport $p$ by every airline: 
-\begin{equation}
-E(p) = \{rsl | (r=p \lor s=p) \land \exists_{l \in L}:rsl \in E \}
-\end{equation}
-The Edges of the graph are thus triplets of a source airport, destination airport and an airline.
-There may be multiple edges between two airports pointing in different directions and/or operated by different airlines.
-We could assume an equal distribution of the flows among the edges.
-But we chose trying to be closer to reality by weighting the flow of an edge between two airports $p$ and $q$, that is operated by airline $l$, by the geometric mean of the number of edges airline $l$ operates at airport $p$ and number of edges airline $l$ operates at airport $q$:
-\begin{equation}
-\begin{aligned}
-&flow(pql) =\\
-={}&avgFlow(pq)  
-* noe(pq) 
-* weight(pql) 
-\end{aligned}
-\end{equation}
-where $noe(pq)$ is the number of edges between airport $p$ and $q$ and $weight(pql)$ is defined as follows: 
-\begin{equation}
-\begin{aligned}
-&weight(pql) = \dfrac{\sqrt{degree_{l}(p) * degree_{l}(q)}}{pnws(pql)}
-\end{aligned}
-\end{equation}
-where the $pnws(pq)$ (Pre Normalization Weight Sum) is just the sum of the non-normalized weights of all the routes from different airlines to normalize the weights. 
-\begin{equation}
-\begin{aligned}
-&pnws(pq) = \\
-={}&\displaystyle\sum_{rsm \in E(pq)}(\sqrt{degree_{m}(r) * degree_{m}(s)})
-\end{aligned}
-\end{equation}
-where $degree_l(p)$ is the degree of airport $p$ in airline $l$'s subgraph, i.e. number of edges from and to airport $p$ operated by airline $l$.
+\begin{center}
+\begin{table}[ht]	
+ \begin{tabular}{| c | c | c |}
+ \hline
+ Diameter & Total Distance & Average Distance \\ [0.5ex]
+ \hline
+ 18834 & 126681574 & 1889.72 \\
+ \hline
+ \end{tabular}
+\caption{Distance Metrics of the Network}
+\label{Tab:distance_metrics}	 
+\end{table}
+\end{center}
 
-The ratios we choose here will stay intact over the course of the iterations in the next part of the algorithm. 
-In every iteration, we traverse all airports and for every airport we calculate the sum of current flows values of all routes. 
-\begin{equation}
-\begin{aligned}
-flowSum(p) = \displaystyle\sum_{pql \in E \cup pu \in E}flow_{pql}
-\end{aligned}
-\end{equation}
-Difference between the patronage and the current sum of passenger flows of incoming and outgoing routes. 
-Then, for each airport we calculate the difference between its patronage and the current sum of flows.
-\begin{equation}
-\begin{aligned}
-flowDiff(p) = patronage(p) - flowSum(p) 
-\end{aligned}
-\end{equation}
-With this information given, we can now calculate for every edge $pql$ the change in its flow. 
-\begin{equation}
-\begin{aligned}
-\forall_{pql \in E(p)}: & \\
-& \Delta flow(pql) = & \\ 
-& ={} \dfrac{flow(pql)}{flowSum(p)}flowDiff(p) \\
-& +{} \dfrac{flow(pql)}{flowSum(q)}flowDiff(q) \\
-\end{aligned}
-\end{equation}
-and the more perfect flows for the edges and starting point for the next itaration are
-\begin{equation}
-\begin{aligned}
-\forall_{pql \in E(p)}: & \\
-& flow'(pql) = flow_{abo} + \Delta flow(pql)
-\end{aligned}
-\end{equation}
-
-In order to look at the results of this algorithm we introduce a measure 
-\begin{equation}
-flowDeviation(p) = ln(flowSum(p)/patronage(p))
-\end{equation}
-it expresses how well the sum of estimated flows match the patronage, that we know for the airport.
-If the flows are half the patronage the absolute value of $flowDeviation$ will be the same as when the current flows are twice the actual patronage number.
-We compare the results between estimating the patronages based on the runway sizes Figure~\ref{fig:flow_deviation_runway} and estimating the patronages based on neighboring airports Figure~\ref{fig:flow_deviation}.
-The blue line shows the $flowDeviation$ distribution of the initial flow values.
-The other almost totally overlapping lines show the $flowDeviation$ distribution after a couple of iterations.
-
-The bad results of the estimations when estimating patronage values from runways stem from constellations like in Figure~\ref{fig:impossible_flows}, when choosing flows to match the patronage values are impossible.
+We currently do not have the ability to calculate centrality parameters like Eigenvector, Closeness or Betweenness Centrality for a Multidirected Graph.
+So we will be mainly looking at Degree Centrality of the entire network as shown in Figure~\ref{fig:degree_centrality}.
+This is because Degree Centrality is the only Centrality available for Multiple Directed Graphs.
 
@@
         \centering
-	\includegraphics[width=76mm]{imgs/flow_estimation_runway_approach_deviation.png}
+        \includegraphics[width=80mm]{imgs2/results/degree_centrality_whole_network.png}
         \caption{
-Estimated flows when estimating patronage based on the runway size }
-	\label{fig:flow_deviation_runway}
+The degree centrality of the entire network}
+        \label{fig:degree_centrality}
 \end{figure}
 
-\begin{figure}
-	\centering
-	\includegraphics[width=76mm]{imgs/results/flow_estimation_120_iterations.png}
-	\caption{
-Estimated flows when estimating patronage based on neighboring airport's patronage}
-	\label{fig:flow_deviation}
-\end{figure}
+The degree centrality is given by the formula:
+\begin{equation}
+	Degree Centrality=d_i/(n-1)
+\end{equation}
 
-The complete algorithm for passenger flow estimation can be found in the repository: ./scripts/estimate-passenger-flows.py
+Just by analysing the graph, we can say that the degree centrality distributrion is following the Power Law Distribution.
 
-\section{Basic Network Analysis}
-
-\section{Airline Subgraph Analysis \& Comparison}
+\section{Airline Subnetwork Analysis \& Comparison}
+W
 
@@
 
-The possibility to provide convenient on-line connections to clients is an important factor that drives welfare gains through airline cooperation according to E.
+The possibility to provide convenient on-line connections to clients is an important factor that drives welfare gains through ailine cooperation according to E.
 E.
@@
 
-\section*{Acknowledgments}
+\section*{Acknowledgements}
 

### 2020-02-15 analysis/mainMetrics.py

@@ -1,0 +1,30 @@
+import networkx as nx
+import sqlite3
+import analysis
+import matplotlib.pyplot as plt
+import scipy as sp
+
+conn = sqlite3.connect('/home/sai/Documents/WiSe 2019-2020/Network Economics/Case '
+                       'Study/network-economics-case-study/db.db')
+cursor = conn.cursor()
+
+cursor.execute("SELECT * FROM Routes")
+rows = cursor.fetchall()
+print("Graph is going to be created")
+G = nx.MultiDiGraph()
+for row in rows:
+    G.add_edge(row[3], row[5], weight=int(row[len(row) - 2]), flow=int(row[len(row) - 1]))
+print("Graph has been created")
+
+distDetails = []
+distEdgeData = G.edges.data('weight')
+sortedDistEdgeData = sorted(distEdgeData, key=lambda x: x[2], reverse=True)
+listEdges = []
+for edge in sortedDistEdgeData:
+    listEdges.append(edge[2])
+distDetails["dist_diameter"] = sortedDistEdgeData[0]
+distDetails["totalDistance"] = G.size(weight='weight')
+distDetails["avgDistance"] = G.size(weight='weight') / len(sortedDistEdgeData)
+
+print(distDetails.items())
+

### 2020-02-18 paper/main.tex
new graphs in report

--- 2020-02-12 paper/main.tex
@@
 \end{figure}
+
 \section{Basic Network Analysis}
+Initially, we would like to analyse the entire worldwide airline network, and provide some insights regarding the airline industry.
+Since a particular route could be provided by multiple Airline Companies, the final network that we come up with is a Multiple Directed Network.
+The attributes of each edge in this network included both the geometrical distance and the average passenger flow of that route (edge). 
+As we can see from the Table~\ref{Tab:distance_metrics}, the diameter of the entire network is given along with the Total Distance of the routes and the Average Distance of routes in a network.
+
+\begin{center}
+\begin{table}[ht]	
+ \begin{tabular}{| c | c | c |}
+ \hline
+ \textbf{Diameter (km)} & \textbf{Total Dist.(km)} & \textbf{Average Dist.(km)} \\ [0.5ex]
+ \hline
+ 18834 & 126681574 & 1889.72 \\
+ \hline
+ \end{tabular}
+\caption{Distance Metrics of the Network}
+\label{Tab:distance_metrics}	 
+\end{table}
+\end{center}
+
+We currently do not have the ability to calculate centrality parameters like Eigenvector, Closeness or Betweenness Centrality for a Multidirected Graph.
+So we will be mainly looking at Degree Centrality of the entire network as shown in Figure~\ref{fig:degree_centrality}.
+This is because Degree Centrality is the only Centrality available for Multiple Directed Graphs.
+
+\begin{figure}
+        \centering
+        \includegraphics[width=80mm]{imgs2/results/degree_centrality_whole_network.png}
+        \caption{
+The degree centrality of the entire network}
+        \label{fig:degree_centrality}
+\end{figure}
+
+The degree centrality is given by the formula:
+\begin{equation}
+	Degree Centrality=d_i/(n-1)
+\end{equation}
+
+Just by analysing the graph, we can say that the degree centrality distributrion is following the Power Law Distribution.
 
 \section{Airline Subgraph Analysis \& Comparison}
+
+Airline Networks can be mainly divided into two different types of networks. Full Service Airlines which are also called as Legacy Carriers, and Low Cost Airlines or Low Cost Carriers.  
+Full Service Airlines generally provide free baggage allowance, meals, drinks, seat selection and in-flight entertainment at no extra charge.
+Low Cost Carriers will usually collect ancillary revenue for all or most of the above these amentities.
+Most of the time, Low Cost Carriers operate in a specific regions.
+These specific regions could be within countries, or within continents, or within specific part of the continents.
+
+\begin{figure}
+        \centering
+        \includegraphics[width=80mm]{imgs2/united_airline_network.png}
+        \caption{
+Network of United Airlines}
+        \label{fig:united_airline}
+\end{figure}
+
+\begin{figure}
+        \centering
+        \includegraphics[width=80mm]{imgs2/american_airline_network.png}
+        \caption{
+Network of American Airlines}
+        \label{fig:american_airline}
+\end{figure}
+
+Long haul low cost carriers are provided by very few carriers in the world, as it is not feasible to offer long routes with low cost and also high frequency, according to Robert L.
+Candall, former CEO of American Airlines.\cite{long_haul_lcc_model}
+The only example we have of a long haul low cost carrier is Norwegian Airlines, as they offer flights from Scandinavia to different cities in the United States.
+But this is more an exception, than the norm.
+For the long haul low cost carriers to survive and adapt, they must continue to innovate.
+Their business models should focus on three new emerging carrier types: Network, Product and Price Specialist, according to John G.Wensveen and Ryan Leick.\cite{long_haul_lcc_new_model}
+
+Before we look at the differences in the network parameters of these two types of airlines, there are major differences in the network architecture itself.
+While the major Full Service Airlines often have the Network Type of "Hub and Spoke", the Low Cost Carriers are known to have Point to Point Network Type, according to research by Cook G.N and Goodwin, J.\cite{airline_network_comparison}
+This "Hub and Spoke" network connection can be seen in the network graph of United Airlines and American Airlines given in Figure~\ref{fig:united_airline} and Figure~\ref{fig:american_airline} respectively.
+These two airlines are prime example of Full Service Airlines.
+
+Similarly we see the "Point to Point" Network in Low Cost Carriers like Ryan Air in Figure~\ref{fig:ryan_air} and Southwest Airlines in Figure~\ref{fig:southwest_airline}.
+
+\begin{figure}
+        \centering
+        \includegraphics[width=80mm]{imgs2/ryan_air_network.png}
+        \caption{
+Network of Ryan Air}
+        \label{fig:ryan_air}
+\end{figure}
+
+\begin{figure}
+        \centering
+        \includegraphics[width=80mm]{imgs2/southwest_airline_network.png}
+        \caption{
+Network of Southwest Airlines}
+        \label{fig:southwest_airline}
+\end{figure}
+
+\begin{table}[ht]
+\begin{center}
+ \begin{tabular}{| c | c |}
+ \hline
+ \textbf{Airline} & \textbf{Diameter (km)} \\ [0.5ex]
+ \hline
+ United Airlines & 12979 \\
+ \hline
+ American Airlines & 14076 \\
+ \hline
+ Delta Airlines & 13581 \\
+ \hline
+ Ryan Air & 3698 \\
+ \hline
+ Southwest Airlines & 3757 \\
+ \hline
+ Air Asia & 2914 \\
+ \hline
+ China Southern & 11637 \\
+ \hline
+ China Eastern & 11896 \\
+ \hline
+ \end{tabular}
+\caption{Diameter of Major Airlines}
+\label{Tab:diameter_metrics}
+\end{center}
+\end{table}
+
+\begin{table}[ht]
+\begin{center}
+ \begin{tabular}{| c | c | c |}
+ \hline
+ \textbf{Airline} & \textbf{Mean (km)} & \textbf{Median (km)} \\ [0.5ex]
+ \hline
+ United Airlines & 2353.69 & 1393 \\
+ \hline
+ American Airlines & 2321.23 & 1371 \\
+ \hline
+ Delta Airlines & 2352.17 & 1341 \\
+ \hline
+ Ryan Air & 1490.21 & 1435.5 \\
+ \hline
+ Southwest Airlines & 1398.37 & 1267 \\
+ \hline
+ Air Asia & 1328.57 & 1254 \\
+ \hline
+ China Southern & 1459.95 & 1127 \\
+ \hline
+ China Eastern & 1427.81 & 1075 \\
+ \hline
+ \end{tabular}
+\caption{Distance Metrics of Major Airlines}
+\label{Tab:distance_airlines}
+\end{center}
+\end{table}
+
+\begin{table}[ht]
+\begin{center}
+ \begin{tabular}{| c | c | c |}
+ \hline
+ \textbf{Airline} & \textbf{Mean Flow} & \textbf{Median Flow} \\ [0.5ex]
+ \hline
+ United Airlines & 85159 & 43286 \\
+ \hline
+ American Airlines & 67983.40 & 47185 \\
+ \hline
+ Delta Airlines & 76345.95  & 47123 \\
+ \hline
+ Ryan Air & 31268.60 & 26857.50 \\
+ \hline
+ Southwest Airlines & 65692.70  & 61590 \\
+ \hline
+ China Southern & 53100  & 43729.50 \\
+ \hline
+ China Eastern & 52610.60  & 43294 \\
+ \hline
+ \end{tabular}
+\caption{Passenger Flow of Major Airlines}
+\label{Tab:passenger_flow_airlines}
+\end{center}
+\end{table}
+
+\begin{figure}
+        \centering
+        \includegraphics[width=80mm]{imgs2/results/united_eigenvalue_centrality.png}
+        \caption{
+Eigenvalue Centrality of United Airlines}
+        \label{fig:united_air_ec}
+\end{figure}
+
+\begin{figure}
+        \centering
+        \includegraphics[width=80mm]{imgs2/results/delta_eigenvalue_centrality.png}
+        \caption{
+Eigenvalue Centrality of Delta Airlines}
+        \label{fig:delta_air_ec}
+\end{figure}
+
+\begin{figure}
+        \centering
+        \includegraphics[width=80mm]{imgs2/results/american_eigenvalue_centrality.png}
+        \caption{
+Eigenvalue Centrality of American Airlines}
+        \label{fig:american_air_ec}
+\end{figure}
+
+\begin{figure}
+        \centering
+        \includegraphics[width=80mm]{imgs2/results/ryan_eigenvalue_centrality.png}
+        \caption{
+Eigenvalue Centrality of Ryan Air}
+        \label{fig:ryan_air_ec}
+\end{figure}
+
+\begin{figure}
+        \centering
+        \includegraphics[width=80mm]{imgs2/results/southwest_eigenvalue_centrality.png}
+        \caption{
+Eigenvalue Centrality of Southwest Airlines}
+        \label{fig:southwest_air_ec}
+\end{figure}
+
+\begin{figure}
+        \centering
+        \includegraphics[width=80mm]{imgs2/results/chinasouthern_eigenvalue_centrality.png}
+        \caption{
+Eigenvalue Centrality of China Southern Airlines}
+        \label{fig:chinasouthern_air_ec}
+\end{figure}
+
+\begin{figure}
+        \centering
+        \includegraphics[width=80mm]{imgs2/results/chinaeastern_eigenvalue_centrality.png}
+        \caption{
+Eigenvalue Centrality of China Eastern Airlines}
+        \label{fig:chinaeastern_air_ec}
+\end{figure}
 

### 2020-02-18 scripts/draw-alliances.py
draw alliances on a map

@@ -1,0 +1,89 @@
+import networkx as nx
+import plotly.graph_objects as go
+
+# local modules 
+from network_loaders import loadAirlineNetwork
+
+alliances = {}
+joint = None 
+
+alliance_names = ['oneworld', 'skyteam', 'staralliance', 'vanilla']
+
+for alliance_name in alliance_names:
+	print(alliance_name)
+	f = open("../data/alliances/" + alliance_name)
+
+	alliance = None
+	for airline_id in map(lambda line: line.strip(), f): 
+		S = loadAirlineNetwork(airline_id)
+		if alliance == None:
+			alliance = S
+		else: 
+			alliance = nx.compose(alliance, S) 
+
+	alliances[alliance_name] = alliance
+
+	if joint == None: 
+		joint = alliance
+	else: 	
+		joint = nx.compose(joint, alliance) 
+
+fig = go.Figure()
+lons = []
+lats = []
+texts = []
+for airport_id in joint.nodes: 
+	airport = joint.nodes[airport_id]
+	lons.append(airport["longitude"])
+	lats.append(airport["latitude"])
+	texts.append(airport["name"])
+
+fig.add_trace(go.Scattergeo(
+	lon=lons,
+	lat=lats,
+	marker=dict(
+		size=2, 
+		color='rgb(55,55,55)'
+	),
+	name="airports"
+))
+
+color = dict(
+	oneworld = 'rgb(155,0,105)',
+	skyteam = 'rgb(5,14,155)',
+	staralliance = 'rgb(105,105,105)', 
+	vanilla = 'rgb(160,160,0)'
+)
+
+for alliance_name in alliance_names:
+	alliance = alliances[alliance_name]
+	lons = []
+	lats = []
+	for edge in alliance.edges: 
+			sa = alliance.nodes[edge[0]]
+			da = alliance.nodes[edge[1]]
+			lons = lons + [sa["longitude"], da["longitude"], None]
+			lats = lats + [sa["latitude"], da["latitude"], None]
+	
+	fig.add_trace(go.Scattergeo(
+		lon=lons,
+		lat=lats,
+		mode='lines',
+		line=dict(
+			width=1, 
+			color=color[alliance_name],
+		),
+		opacity=0.5,
+		name=alliance_name
+	))
+
+fig.update_layout(
+	geo=go.layout.Geo(),
+	height=900
+)
+fig.update_geos(
+	resolution=110, 
+	projection_type='natural earth'
+)
+
+fig.show()

### 2020-02-18 scripts/degree_distribution_incl_odd_degrees.py
very simple degree plot for the paper

@@ -1,0 +1,43 @@
+import collections
+import matplotlib.pyplot as plt 
+import numpy as np
+import math
+import scipy.optimize
+
+import network_loader 
+
+network = network_loader.load()
+
+degree_counts = {}
+max_degree = 0
+
+for n, d in network.degree():
+	try:
+		degree_counts[d] += 1
+	except:
+		degree_counts[d] = 1
+	if d > max_degree: 
+		max_degree = d
+
+degrees = []
+nodes = []
+
+for degree_count in degree_counts:
+	degrees.append(degree_count)
+	nodes.append(degree_counts[degree_count])
+	
+degrees = np.array(degrees)
+nodes = np.array(nodes) 
+
+ 
+plt.scatter(degrees, nodes, marker='o', s=10)
+
+plt.xlabel('degree')
+plt.ylabel('number of nodes')
+
+plt.xscale('log')
+plt.yscale('log')
+
+plt.savefig('./results/degree_distribution_incl_odd_degrees.png', dpi=300, bbox_inches='tight')
+plt.show()
+

### 2020-02-18 maps/us-flight-paths-example.py
performance improving plotting of many edges

@@ -26,17 +26,23 @@ fig.add_trace(go.Scattergeo(
     )))
 
 flight_paths = []
+lons = []
+lats = []
 for i in range(len(df_flight_paths)):
-    fig.add_trace(
-        go.Scattergeo(
-            locationmode = 'USA-states',
-            lon = [df_flight_paths['start_lon'][i], df_flight_paths['end_lon'][i]],
-            lat = [df_flight_paths['start_lat'][i], df_flight_paths['end_lat'][i]],
-            mode = 'lines',
-            line = dict(width = 1,color = 'red'),
-            opacity = float(df_flight_paths['cnt'][i]) / float(df_flight_paths['cnt'].max()),
-        )
+    # None interrupts lines and makes it possible to draw multiple disconnected lines.
+    lons += [df_flight_paths['start_lon'][i], df_flight_paths['end_lon'][i], None] 
+    lats += [df_flight_paths['start_lat'][i], df_flight_paths['end_lat'][i], None]
+
+fig.add_trace(
+    go.Scattergeo(
+        locationmode = 'USA-states',
+        lon = lons,
+        lat = lats,
+        mode = 'lines',
+        line = dict(width = 1,color = 'red'),
+        opacity = 0.5 
     )
+)
 
 fig.update_layout(
     title_text = 'Feb. 2011 American Airline flight paths<br>(Hover for airport names)',
@@ -48,7 +54,7 @@ fig.update_layout(
         landcolor = 'rgb(243, 243, 243)',
         countrycolor = 'rgb(204, 204, 204)',
     ),
-	height=700,
+    height=700,
 )
 
 fig.show()

### 2020-02-19 scripts/alliances-game.py
writing an algorithm that finds alliances

@@ -1,0 +1,109 @@
+import sys
+import networkx as nx
+import concurrent.futures
+
+# local modules
+from network_loaders import loadAirlineNetwork
+import largeness
+
+alliances = {}
+
+class Alliance: 
+	def __init__(self, network, airline):
+		self.network = network
+		self.airlines = [airline]
+
+	def name(self): 
+		return '(%s)' % '-'.join(self.airlines)
+
+	def merge(self, other):
+		self.network = nx.compose(self.network, other.network) 
+		self.airlines = self.airlines + other.airlines
+		return self
+
+	def __repr__(self): 
+		return 'alliance' + self.name
+
+def calculateOpportunity(matrix, a, b): 
+	aa = alliances[a]
+	ab = alliances[b]
+	la = largeness.calculateForGraph(aa.network) 
+	lb = largeness.calculateForGraph(ab.network) 
+	c = nx.compose(aa.network, ab.network) 
+	lc = largeness.calculateForGraph(c) 
+	matrix[a][b] = lc / ( la + lb ) 
+
+print('creating initial single member alliances') 
+real_alliance_names = ['oneworld', 'skyteam', 'staralliance', 'vanilla']
+for alliance_name in real_alliance_names: 
+	f = open("../data/alliances/" + alliance_name)
+	for airline_id in map(lambda line: line.strip(), f): 
+		alliance = Alliance(loadAirlineNetwork(airline_id), airline_id) 
+		alliances[alliance.name()] = alliance
+
+opportunity_matrix = {}
+keys = list(alliances.keys())
+tp = concurrent.futures.ThreadPoolExecutor(max_workers=7)
+jobs = []
+jobcount = 0
+for i in keys: 
+	opportunity_matrix[i] = {}
+	for j in keys: 
+		if i == j: 
+			break
+		jobs.append(tp.submit(calculateOpportunity, opportunity_matrix, i, j))
+		jobcount += 1
+donecount = 0
+for job in concurrent.futures.as_completed(jobs):
+	donecount += 1
+	sys.stdout.write('\rinitialize opportunity matrix {0:.1f}%'.format(100 * donecount/jobcount))
+tp.shutdown(wait=True)
+print()
+
+while len(keys) > 4: 
+	highest_opportunity = 0
+	hi = None
+	hj = None
+	for i in keys: 
+		for j in keys:
+			if i == j: 
+				break
[…]

### 2020-02-19 scripts/alliances-game.py
draw real and generated alliances on a map

@@ -1,3 +1,4 @@
+import os
 import sys
 import networkx as nx
 import concurrent.futures
@@ -34,12 +35,16 @@ def calculateOpportunity(matrix, a, b):
 	matrix[a][b] = lc / ( la + lb ) 
 
 print('creating initial single member alliances') 
-real_alliance_names = ['oneworld', 'skyteam', 'staralliance', 'vanilla']
-for alliance_name in real_alliance_names: 
-	f = open("../data/alliances/" + alliance_name)
-	for airline_id in map(lambda line: line.strip(), f): 
-		alliance = Alliance(loadAirlineNetwork(airline_id), airline_id) 
-		alliances[alliance.name()] = alliance
+folder = "../data/alliances"
+real_alliance_names = []
+for f in os.listdir(folder):
+	if os.path.isfile(folder + '/' + f): 
+		real_alliance_names.append(f)
+		print(f) 
+		f = open(folder + '/' + f)
+		for airline_id in map(lambda line: line.strip(), f): 
+			alliance = Alliance(loadAirlineNetwork(airline_id), airline_id) 
+			alliances[alliance.name()] = alliance
 
 opportunity_matrix = {}
 keys = list(alliances.keys())
@@ -99,11 +104,16 @@ while len(keys) > 4:
 
 	opportunity_matrix[i] = new_opportunities[i]
 
-print('\nresults:')
+result_folder = 'results/alliances'
+os.makedirs(result_folder, exist_ok=True) 
+for f in os.listdir(result_folder):
+	os.remove(result_folder + '/' + f) 
 index = 0
 for key in alliances: 
-	print('alliance', index) 
+	f = open(result_folder + ('/gen%i' % index), 'w')
 	index += 1
 	for airline_id in alliances[key].airlines: 
-		print('-', airline_id) 
+		f.write(airline_id + '\n') 
 
+for key in alliances: 
+	f.flush()

### 2020-02-19 scripts/alliances_drawer.py

@@ -1,0 +1,95 @@
+import os
+import networkx as nx
+import plotly.graph_objects as go
+
+# local modules 
+from network_loaders import loadAirlineNetwork
+
+def drawAlliances(folder = "../data/alliances"):
+	print(folder) 
+	alliance_names = []
+	for f in os.listdir(folder):
+		if os.path.isfile(folder + '/' + f): 
+			alliance_names.append(f)
+			print('found airline', f) 
+
+	alliances = {}
+	joint = None 
+
+	for alliance_name in alliance_names:
+		f = open(folder + "/" + alliance_name)
+
+		alliance = None
+		for airline_id in map(lambda line: line.strip(), f): 
+			S = loadAirlineNetwork(airline_id)
+			if alliance == None:
+				alliance = S
+			else: 
+				alliance = nx.compose(alliance, S) 
+
+		alliances[alliance_name] = alliance
+
+		if joint == None: 
+			joint = alliance
+		else: 	
+			joint = nx.compose(joint, alliance) 
+
+	fig = go.Figure()
+	lons = []
+	lats = []
+	texts = []
+	for airport_id in joint.nodes: 
+		airport = joint.nodes[airport_id]
+		lons.append(airport["longitude"])
+		lats.append(airport["latitude"])
+		texts.append(airport["name"])
+
+	fig.add_trace(go.Scattergeo(
+		lon=lons,
+		lat=lats,
+		marker=dict(
+			size=2, 
+			color='rgb(55,55,55)'
+		),
+		name="airports"
+	))
+
+	colors = [ 
+		'rgb(155,0,105)',
+		'rgb(185,140,5)', 
+		'rgb(5,14,155)',
+		'rgb(90,160,0)'
+	]
+	color_index = 0
+	for i, alliance_name in enumerate(alliance_names):
+		alliance = alliances[alliance_name]
+		lons = []
+		lats = []
+		for edge in alliance.edges: 
+				sa = alliance.nodes[edge[0]]
+				da = alliance.nodes[edge[1]]
+				lons = lons + [sa["longitude"], da["longitude"], None]
+				lats = lats + [sa["latitude"], da["latitude"], None]
+		
+		fig.add_trace(go.Scattergeo(
+			lon=lons,
+			lat=lats,
+			mode='lines',
+			line=dict(
+				width=0.45, 
+				color=colors[i % len(colors)],
+			),
+			opacity=0.4,
+			name=alliance_name
[…]

### 2020-02-19 scripts/draw-alliances.py

@@ -1,89 +1,0 @@
-import networkx as nx
-import plotly.graph_objects as go
-
-# local modules 
-from network_loaders import loadAirlineNetwork
-
-alliances = {}
-joint = None 
-
-alliance_names = ['oneworld', 'skyteam', 'staralliance', 'vanilla']
-
-for alliance_name in alliance_names:
-	print(alliance_name)
-	f = open("../data/alliances/" + alliance_name)
-
-	alliance = None
-	for airline_id in map(lambda line: line.strip(), f): 
-		S = loadAirlineNetwork(airline_id)
-		if alliance == None:
-			alliance = S
-		else: 
-			alliance = nx.compose(alliance, S) 
-
-	alliances[alliance_name] = alliance
-
-	if joint == None: 
-		joint = alliance
-	else: 	
-		joint = nx.compose(joint, alliance) 
-
-fig = go.Figure()
-lons = []
-lats = []
-texts = []
-for airport_id in joint.nodes: 
-	airport = joint.nodes[airport_id]
-	lons.append(airport["longitude"])
-	lats.append(airport["latitude"])
-	texts.append(airport["name"])
-
-fig.add_trace(go.Scattergeo(
-	lon=lons,
-	lat=lats,
-	marker=dict(
-		size=2, 
-		color='rgb(55,55,55)'
-	),
-	name="airports"
-))
-
-color = dict(
-	oneworld = 'rgb(155,0,105)',
-	skyteam = 'rgb(5,14,155)',
-	staralliance = 'rgb(105,105,105)', 
-	vanilla = 'rgb(160,160,0)'
-)
-
-for alliance_name in alliance_names:
-	alliance = alliances[alliance_name]
-	lons = []
-	lats = []
-	for edge in alliance.edges: 
-			sa = alliance.nodes[edge[0]]
-			da = alliance.nodes[edge[1]]
-			lons = lons + [sa["longitude"], da["longitude"], None]
-			lats = lats + [sa["latitude"], da["latitude"], None]
-	
-	fig.add_trace(go.Scattergeo(
-		lon=lons,
-		lat=lats,
-		mode='lines',
-		line=dict(
-			width=1, 
-			color=color[alliance_name],
-		),
-		opacity=0.5,
-		name=alliance_name
-	))
-
-fig.update_layout(
-	geo=go.layout.Geo(),
-	height=900
-)
-fig.update_geos(
-	resolution=110, 
-	projection_type='natural earth'
-)
-
-fig.show()

### 2020-02-19 scripts/draw-generated-alliances.py

@@ -1,0 +1,3 @@
+import alliances_drawer
+
+alliances_drawer.drawAlliances('results/alliances')

### 2020-02-19 scripts/draw-real-alliances.py

@@ -1,0 +1,3 @@
+import alliances_drawer
+
+alliances_drawer.drawAlliances('../data/alliances')

### 2020-02-19 paper/main.tex
joined some tables, started work on 'largeness'

@@
 	\centering
-	\caption{patronage data availability - worst countries}
+	\caption{Worst patronage data availability on Wikidata}
 	\label{tab:patr_av_worst}
@@
 \begin{center}
- \begin{tabular}{| c | c |}
+ \begin{tabular}{| l | r | r | r |}
  \hline
- \textbf{Airline} & \textbf{Diameter (km)} \\ [0.5ex]
+ \textbf{Airline} & \textbf{Mean} & \textbf{Median} & \textbf{Diam.} \\ 
  \hline
- United Airlines & 12979 \\
+ United & 2353.69 & 1393 & 12979 \\
  \hline   
- American Airlines & 14076 \\
+ American & 2321.23 & 1371 & 14076 \\
  \hline   
- Delta Airlines & 13581 \\
+ Delta & 2352.17 & 1341 & 13581 \\
  \hline   
- Ryan Air & 3698 \\
+ Ryan Air & 1490.21 & 1435 & 3698 \\
  \hline   
- Southwest Airlines & 3757 \\
+ Southwest & 1398.37 & 1267 & 3757 \\
  \hline   
- Air Asia & 2914 \\
+ Air Asia & 1328.57 & 1254 & 2914 \\
  \hline   
- China Southern & 11637 \\
+ Ch. Southern & 1459.95 & 1127 & 11637 \\
  \hline   
- China Eastern & 11896 \\
+ Ch. Eastern & 1427.81 & 1075 & 11896 \\
  \hline
  \end{tabular}
-\caption{Diameter of Major Airlines}
-\label{Tab:diameter_metrics}
-\end{center}
-\end{table}
-
-\begin{table}[ht]
-\begin{center}
- \begin{tabular}{| c | c | c |}
- \hline
- \textbf{Airline} & \textbf{Mean (km)} & \textbf{Median (km)} \\ [0.5ex]
- \hline
- United Airlines & 2353.69 & 1393 \\
- \hline
- American Airlines & 2321.23 & 1371 \\
- \hline
- Delta Airlines & 2352.17 & 1341 \\
- \hline
- Ryan Air & 1490.21 & 1435.5 \\
- \hline
- Southwest Airlines & 1398.37 & 1267 \\
- \hline
- Air Asia & 1328.57 & 1254 \\
- \hline
- China Southern & 1459.95 & 1127 \\
- \hline
- China Eastern & 1427.81 & 1075 \\
- \hline
- \end{tabular}
-\caption{Distance Metrics of Major Airlines}
+\caption{Mean, Median and Diameter of subgraphs of major airlines (all numbers in kilometers)}
 \label{Tab:distance_airlines}
@@
 \begin{center}
- \begin{tabular}{| c | c | c |}
+ \begin{tabular}{| l | r | r |}
  \hline
@@
  \hline
- United Airlines & 85159 & 43286 \\
+ United & 85159 & 43286 \\
  \hline
- American Airlines & 67983.40 & 47185 \\
+ American & 67983.40 & 47185 \\
  \hline
- Delta Airlines & 76345.95  & 47123 \\
+ Delta & 76345.95  & 47123 \\
  \hline
@@
  \hline
- Southwest Airlines & 65692.70  & 61590 \\
+ Southwest & 65692.70  & 61590 \\
  \hline
- China Southern & 53100  & 43729.50 \\
+ Ch. Southern & 53100  & 43729.50 \\
  \hline
- China Eastern & 52610.60  & 43294 \\
+ Ch. Eastern & 52610.60  & 43294 \\
  \hline
@@
 
-\section{Reality Check: Vanilla Airlines}
+In this paper Bailey et al.
+emphasize the importance of network effects for airline competition.
+The mention Carlton, Landes and Posner \cite{costs-and-benefits-of-airline-mergers}, who found out, that when there is an intermediate stop on a trip, consumer welfare is higher, if both segments are operated by the same airline.
+"The connection and navigation times within the hub airport are shorter and the hassle is less than with a change of carrier" \cite{airline_consolidation_and_consumer_welfare}. 
+Think for example about the hassle that arises if you have booked two segments independently and you miss the seccond flight due to a delay of the first flight.
+
+There is a welfare gain, when a connection from A to B could previously only be achieved by booking a flight with two different airlines, can now be achieved by booking two flights from a single airline within one ticket.
+It is better for a consumer, to buy one ticket for a flight \mbox{A$\rightarrow$B$\rightarrow$C} from a single airline 
+Than buying two tickets for \mbox{A$\rightarrow$B} and \mbox{B$\rightarrow$C} from two distinct airlines.
+
+We construct a measure that captures this welfare gain for a potential merge of two airlines $l$ and $m$.
+
+For both airports, we first caculate the sum of supported length-2 flights weighted by the "popularity" of the two connected airports, as the welfare gain scales with the demand for this connection.
+
+\begin{equation}
+L2Largeness(airline) = \sum{
+\end{equation}
+
+\begin{equation}
+Opportunity = 
+\end{equation}
+
+\section{Outlook: Improving the metric}
 

### 2020-02-19 paper/main.tex
hotfix :P latex

@@
 \DeclareMathOperator{\flowDiff}{flowDiff}
+\DeclareMathOperator{\Largeness}{Largeness}
+\DeclareMathOperator{\Potential}{Potential}
 
@@
 
-We construct a measure that captures this welfare gain for a potential merge of two airlines $l$ and $m$.
+We construct a metric that captures this welfare gain for a potential merge of two airlines $l$ and $m$.
 
-For both airports, we first caculate the sum of supported length-2 flights weighted by the "popularity" of the two connected airports, as the welfare gain scales with the demand for this connection.
+First, we define a $\Largeness_{2}$ of an airline, that is the sum of all length-2 flights operated by this airline, weighted by the "popularity" of the two connected airports.
+We weight by the "popularity", because the welfare gain from a possibility to book a length-2 flight with a single ticket scales with the demand for this connection.
 
 \begin{equation}
-L2Largeness(airline) = \sum{
+\Largeness_{2}(l) = \sum{p,r \in P,\exists_{q}: pql \in E \and qrl \in E}: \sqrt(\patronage(p) * \patronage(r))
 \end{equation}
 
+To assess the potential of a merge $\Potential(l,m)$ we divide the Largeness of the joint airline network by the sum of the Largenesses of the separate airline networks.
+
 \begin{equation}
-Opportunity = 
+\Potential(l,m) = \dfrac{\Largeness_{2}(l \cup m)}{\Largeness_{2}(l) + \Largeness_{2}(m)} 
 \end{equation}

### 2020-02-19 paper/main.tex
removed big images and added new ones

@@
         \centering
-        \includegraphics[width=80mm]{imgs2/results/united_eigenvalue_centrality.png}
+        \includegraphics[width=80mm]{imgs2/results/eigenvector_centrality_distribution.png}
         \caption{
-Eigenvalue Centrality of United Airlines}
-        \label{fig:united_air_ec}
+Eigenvector Centrality Distribution}
+        \label{fig:eigen_distr}
 \end{figure}
@@
         \centering
-        \includegraphics[width=80mm]{imgs2/results/delta_eigenvalue_centrality.png}
+        \includegraphics[width=80mm]{imgs2/results/closeness_centrality_distribution.png}
         \caption{
-Eigenvalue Centrality of Delta Airlines}
-        \label{fig:delta_air_ec}
+Closeness Centrality Distribution}
+        \label{fig:closeness_distr}
 \end{figure}
@@
         \centering
-        \includegraphics[width=80mm]{imgs2/results/american_eigenvalue_centrality.png}
+        \includegraphics[width=80mm]{imgs2/results/geometrical_distance_distribution.png}
         \caption{
-Eigenvalue Centrality of American Airlines}
-        \label{fig:american_air_ec}
-\end{figure}
-
-\begin{figure}
-        \centering
-        \includegraphics[width=80mm]{imgs2/results/ryan_eigenvalue_centrality.png}
-        \caption{
-Eigenvalue Centrality of Ryan Air}
-        \label{fig:ryan_air_ec}
-\end{figure}
-
-\begin{figure}
-        \centering
-        \includegraphics[width=80mm]{imgs2/results/southwest_eigenvalue_centrality.png}
-        \caption{
-Eigenvalue Centrality of Southwest Airlines}
-        \label{fig:southwest_air_ec}
-\end{figure}
-
-\begin{figure}
-        \centering
-        \includegraphics[width=80mm]{imgs2/results/chinasouthern_eigenvalue_centrality.png}
-        \caption{
-Eigenvalue Centrality of China Southern Airlines}
-        \label{fig:chinasouthern_air_ec}
-\end{figure}
-
-\begin{figure}
-        \centering
-        \includegraphics[width=80mm]{imgs2/results/chinaeastern_eigenvalue_centrality.png}
-        \caption{
-Eigenvalue Centrality of China Eastern Airlines}
-        \label{fig:chinaeastern_air_ec}
+Geometrical Distance Distrubution}
+        \label{fig:geometric_distr}
 \end{figure}

### 2020-02-19 paper/main.tex
changes in latex and citations

@@
 
+We can also appreciate these major differences by analysing various parameters of the network.
+As shown in Table~\ref{Tab:distance_airlines}, we can see that the Full Service Airlines like United Airlines, American Airlines and Delta Airlines, offer routes over really long distances.
+That is the reason why the geometric distance diameters of these airline networks are easily over 12000 kms.
+On the other hand, Low Cost Carriers always offer routes within a certain region, such as only within Europe (Ryan Air) or only within United States (Southwest Airlines).
+And as expected, the diameter of these airline networks are below 4000 kms.
+
+The differences are also apparent when we look at the mean geometric distance of all the routes offered by a particular airline.
+Full Service Carriers show an average route distance of around 2300 kms, while the Low Cost Carriers show that their average route distance is about 1400 kms, which is significantly lower.
+
+We would also like to point out the case of China Southern Airlines and China Eastern Airlines.
+Looking at only the diameter, we can conclude that the Network is as large as United or Delta Airlines.
+But when we look at the mean, they are only around 1400 kms, which represent airlines like RyanAir or Southwest Airlines.
+This discrepancy can be explained by analysing the median geometric distance of these networks.
+These Chinese Airlines have a median of around 1100 kms, which means they have a lot of routes which are within China region only. 
+And looking at the full network, we can also say that, the main reason their diameter is over 12000 kms is because they had recently started to offer few routes to countries like Canada, United States and Germany.
+Although these are large distances, due to high number of local routes within China, the mean route length of this network, turns out to be much more lesser and comparable to Low Cost Carriers.
+
 \begin{table}[ht]
@@
 
+Figure~\ref{fig:geometric_distr} provides us the geometric route distance distribution for airlines United, Lufthansa, RyanAir and Southwest.
+Here too, there is an apparent distinction between the Full Service Airlines and the Low Cost Carriers.
+Ryan Air and Southwest offer so many routes around 1000 km range, that the peak of their distribution is also around that value.
+And of course, their routes stop at a maximum distance of around 4000 kms. 
+Looking at the Full Service Carriers, though the global peak of the distribution of United and Lufthansa is also around the same distance of 1000 kms, we can see that there is a second small peak at around 6000 kms.
+This is nothing but the average route distance for Transatlantic flights between United States and Europe.
+Both of these airlines offer a considerable number of these routes, that it shows in the distribution curve distinctly.
+
+The centrality distributions (both eigenvector and closeness) of these four airlines also provide us with deep insights into their route network. 
+We see that in both the Figures~\ref{fig:eigen_distr} and ~\ref{fig:closeness_distr}, Ryan Air and Southwest have more airports with higher centrality value.
+We could say that the centrality of their network is distributed across many airports, instead of relying on few airports with really high centrality values. 
+The scenario of having few airports with really high centrality value is seen in the case of Full Service Airlines Lufthansa and United Airlines.
+They have high number of airports with low centrality, and few select airports with high centrality values.
+If we look at the network diagram that was previously shown in Figure~\ref{fig:united_airline}, it is apparent that these high centrality airports are basically the hubs of these networks.
+
 \section{Airline Cooperation Opportunity}
@@
 
+The main metric of our analysis $\Largeness_{2}$, is currently dependent on Patronages in each airport and the routes available for each airline.
+Though it already results in providing results which are close to the real world, we can still improve it with few changes in the metric or data.
+With access to the exact population data for each airport, the results would be more accurate.
+
+Another way to improve the metric, is bringing in the centrality of each airport as a weighting factor in the analysis, especially the eigenvector centrality. 
+Unlike degree centrality, which only looks at the number of connections or neighbours for one particular airport, eigenvector centrality looks at both the number, and the centrality of the neighbours for each airport.\cite{eigenvector_centrality}
+There is a not insignificant differences between the patronages of each airport and the eigenvector centrality of each airport in our data, as shown in Figure~\ref{fig:patronage_eigenvector}.
+Thus, considering eigenvector of each airport and using it in a new metric could provide us with different results, from what we achieved through$\Largeness_{2}$ metric. 
+We should also look at the interactions in the network, from the side of airports. Airports also have a significant amount of bargaining power, since they rent their space to be used by the airlines.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=80mm]{imgs2/results/patronage_eigenvector.png}
+	\caption{
+	Patronage vs Eigenvector Distrubution}
+\label{fig:patronage_eigenvector}
+\end{figure}
+
+In the real world, profit of each airlines also plays a major factor in the formation of alliances.
+The typical cost of the airlines are divided into three categories: Flight (Direct) Operating Costs as 50\%, Ground Operating Costs as 30\% and System Operating Costs as 20\%.
+\cite{airline_operating_cost}
+Out of the above three categories, Ground Operating Costs, are especially related to fees to be paid to airports such as aircraft landing fees and reservation charges. 
+Having a coalition with many airlines together, would increase the bargaining power of these alliances, and help in reducing the costs to be paid to these airports.
+
 \section*{Acknowledgments}

### 2020-02-19 paper/main.tex
describing largeness metric

--- 2020-02-19 paper/main.tex
@@
 \DeclareMathOperator{\avgFlow}{avgFlow}
-\DeclareMathOperator{\patronage}{patronage}
+\DeclareMathOperator{\patronage}{patr}
 \DeclareMathOperator{\flow}{flow}
@@
 \DeclareMathOperator{\flowDiff}{flowDiff}
-\DeclareMathOperator{\Largeness}{Largeness}
-\DeclareMathOperator{\Potential}{Potential}
+\DeclareMathOperator{\Largeness}{largeness}
+\DeclareMathOperator{\Potential}{potential}
+\DeclareMathOperator{\WEVC}{WEVC}
+\DeclareMathOperator{\Nodes}{Nodes}
 
@@
  \hline
- \textbf{Diameter (km)} & \textbf{Total Dist.(km)} & \textbf{Average Dist.(km)} \\ [0.5ex]
+ \textbf{Diameter} & \textbf{Total Dist.} & \textbf{Average Dist.} \\ 
  \hline
@@
  \end{tabular}
-\caption{Distance Metrics of the Network}
+\caption{Distance Metrics of the Network in km}
 \label{Tab:distance_metrics}	 
@@
  \hline
- \textbf{Airline} & \textbf{Mean Flow} & \textbf{Median Flow} \\ [0.5ex]
+ \textbf{Airline} & \textbf{Mean Flow} & \textbf{Median Flow} \\ 
  \hline
@@
 
-\begin{figure}
-        \centering
-        \includegraphics[width=80mm]{imgs2/results/eigenvector_centrality_distribution.png}
-        \caption{
-Eigenvector Centrality Distribution}
-        \label{fig:eigen_distr}
-\end{figure}
-
-\begin{figure}
-        \centering
-        \includegraphics[width=80mm]{imgs2/results/closeness_centrality_distribution.png}
-        \caption{
-Closeness Centrality Distribution}
-        \label{fig:closeness_distr}
-\end{figure}
-
-\begin{figure}
-        \centering
-        \includegraphics[width=80mm]{imgs2/results/geometrical_distance_distribution.png}
-        \caption{
-Geometrical Distance Distrubution}
-        \label{fig:geometric_distr}
-\end{figure}
-
-\section{Airline Cooperation Opportunity}
+\section{Airline Cooperation Portential}
 
@@
 
-We construct a metric that captures this welfare gain for a potential merge of two airlines $l$ and $m$.
+We construct a simple but powerfull metric that captures this welfare gain for a potential merge of two airlines $l$ and $m$.
 
@@
 \begin{equation}
-\Largeness_{2}(l) = \sum{p,r \in P,\exists_{q}: pql \in E \and qrl \in E}: \sqrt(\patronage(p) * \patronage(r))
+\begin{aligned}
+ & \Largeness_{2}(l) = \\
+= & \displaystyle\sum_{p,r \in P,\exists_{q}: pql \in E \and qrl \in E}: \sqrt(\patronage(p) * \patronage(r))
+\end{aligned}
 \end{equation}
@@
 \begin{equation}
-\Potential(l,m) = \dfrac{\Largeness_{2}(l \cup m)}{\Largeness_{2}(l) + \Largeness_{2}(m)} 
+\begin{aligned}
+& \Potential(l,m) = \\
+= & \dfrac{\Largeness_{2}(l \cup m)}{\Largeness_{2}(l) + \Largeness_{2}(m)} 
+\end{aligned}
 \end{equation}
 
+Imagine the merge of two airlines yields many new 2-segment flight routes (look at the example in Figure~\ref{fig:potential-example}.
+If there is already a big overlap between the networks, $\Potential(l,m)$ might even be $< 1$ and thus discourage a merger or cooperation\footnote{this aspect of the $\Largeness$ metric might deserve criticism.
+See section "Outlook" for details.}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=76mm]{imgs/potential-example.png}
+	\caption{
+The merger of the blue and green airline networks yields six additional 2-segment connections}
+	\label{fig:potential-example}
+\end{figure}
+
+Because airlines from the same alliance can offer 2-segment flights in one ticket just as merged airlines can, this metric is also applicable for cooperation between airlines or alliance forming.
+
+With this metric at hand, we can give answers to questions like:
+
+"Which alliance should airline X join?"
+"Which airlines should form alliances?"
+
+We don't linger on small questions like this and jump right into reorganizing the airline alliance landscape\footnote{this wording is supposed to be funny and caricaturing.
+Obviously, the factors that lead to forming of alliances are incredibly diverse ranging from historical reasons to interpersonal reasons, and we do not expect that a generated alliance landscape would exactly return the real alliances landscape, that we observe today.
+But we are looking for meta similarities, that describe the characteristics of an alliance landscape.
+As we assume $\Largeness_{2}$ to be an important factor in alliance formation, we a curious to find out which similarities we will be able to spot}.
+We implemented an algorithm that merges one airline with another, until only $N$ are left.
+In each step, the two arilines $l$ and $m$ are merged, that have the highest $\Potential$.
+
+We plot the result on a world map (Figure~\ref{fig:generated-alliance-map}) and compare it to the real alliance landscape (Figure~\ref{fig:real-alliance-map}.
+An remarkable similarity between the generated alliance landscape and the real one, is that one big alliance (green) is covering a lot of flights between the US, Europe and China, but is not much active in South America, South Africa, Australia or New Zealand.
+It also does not operate much in Canada in both the generated and real alliances landscape.
+As expected, there are also differences: For example the generated alliance Landscape suggests spanish speaking South American Countries to be in the same alliance and have Brazilian oparators close to the green alliance, while in real life Buenos Aires is tied to the green alliance (Skyteam) while Brazil get's supplied by a mix of alliances.
+Japan for example belongs to Staralliance in the realworld while in the generated landscape it's a part of big green alliance.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=76mm]{imgs/generated-alliance-map.png}
+	\caption{
+The generated alliance landscape.
+Different colors mean different alliances.
+Green, Blue, Purple, Yellow.
+(Be aware, that by layering the networks of the different alliances on top of each other and routes in a higher layer covering the lower levels, the perception might be distorted.)}
+	\label{fig:generated-alliance-map}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=76mm]{imgs/real-alliance-map.png}
+	\caption{
+The real alliance landscape. Skyteam(green), Staralliance(blue), Oneworld(purple), Vanilla(yellow)}
+	\label{fig:real-alliance-map}
+\end{figure}
+
 \section{Outlook: Improving the metric}
+The $\Largeness$ metric could be improved.
+Right now, when two airlines have the same 2-segment connections, after joining the network, those connections will be counted only once.
+There is no clear reasoning why these overlaps should discourage a merger.
+
+A very promising different approach to capturing welfare that arises from additional single-ticket multi-segment flights through a merger or cooperation between airlines, is to look at the sum of the product of the weighted eigenvector centralities of common airports of the two merge candidates.
+
+$\cap$
+
+\begin{equation}
+\begin{aligned}
+& \Potential_{\WEVC}(l, m) = \\
+ = & \sum_{p \in \Nodes(l \cap m)}: \WEVC_{l}(p) * \WEVC_{m}(p)
+\end{aligned}
+\end{equation}
+
+where $\Nodes(l \cap m)$ are all the common nodes of airlines $l$ and $m$ and $\WEVC_{x}(p)$ is the weighted eigenvector centrality of airport $p$ in airline $x$'s subgraph. 
+The weight for calculating the weighted eigenvector centrality in the subgraph of $x$ is the sum of flows of all edges operated by the respective airline.
 
 \section*{Acknowledgments}
+We thank our professor IProf. Ph.D. konnikova and her Sofia Berdysheva for their brilliance, support and for giving this outstanding course at TUM.
 

### 2020-02-19 paper/main.tex

@@
 Investigations confirm that.
-We disregard these few dataless airports from disconnected subgraphs in the following analyses and thus end up with a network of 3125 airports.
+We disregard these few data-less airports from disconnected subgraphs in the following analyses and thus end up with a network of 3125 airports.
 
@@
 \end{equation}
-and the more perfect flows for the edges and starting point for the next itaration are
+and the more perfect flows for the edges and starting point for the next iteration are
 \begin{equation}
@@
 That's why it ended up with the default patronage value 1523.
-In this constallation it is impossible to choose passenger flows that even remotely satisfy the the patronages of airports with ids 10 and 5446}
+In this constellation it is impossible to choose passenger flows that even remotely satisfy the the patronages of airports with ids 10 and 5446}
 	\label{fig:impossible_flows}
@@
 \section{Basic Network Analysis}
-Initially, we would like to analyse the entire worldwide airline network, and provide some insights regarding the airline industry.
+Initially, we would like to analyze the entire worldwide airline network, and provide some insights regarding the airline industry.
 Since a particular route could be provided by multiple Airline Companies, the final network that we come up with is a Multiple Directed Network.
@@
 
-We currently do not have the ability to calculate centrality parameters like Eigenvector, Closeness or Betweenness Centrality for a Multidirected Graph.
+We currently do not have the ability to calculate centrality parameters like Eigenvector, Closeness or betweenness Centrality for a Multidirected Graph.
 So we will be mainly looking at Degree Centrality of the entire network as shown in Figure~\ref{fig:degree_centrality}.
@@
 
-Just by analysing the graph, we can say that the degree centrality distributrion is following the Power Law Distribution.
+Just by analyzing the graph, we can say that the degree centrality distribution is following the Power Law Distribution.
 
@@
 Full Service Airlines generally provide free baggage allowance, meals, drinks, seat selection and in-flight entertainment at no extra charge.
-Low Cost Carriers will usually collect ancillary revenue for all or most of the above these amentities.
+Low Cost Carriers will usually collect ancillary revenue for all or most of the above these amenities.
 Most of the time, Low Cost Carriers operate in a specific regions.
@@
 \end{figure}
+
+We can also appreciate these major differences by analyzing various parameters of the network.
+As shown in Table~\ref{Tab:distance_airlines}, we can see that the Full Service Airlines like United Airlines, American Airlines and Delta Airlines, offer routes over really long distances.
+That is the reason why the geometric distance diameters of these airline networks are easily over 12000 km.
+On the other hand, Low Cost Carriers always offer routes within a certain region, such as only within Europe (Ryan Air) or only within United States (Southwest Airlines).
+And as expected, the diameter of these airline networks are below 4000 km.
+
+The differences are also apparent when we look at the mean geometric distance of all the routes offered by a particular airline.
+Full Service Carriers show an average route distance of around 2300 km, while the Low Cost Carriers show that their average route distance is about 1400 km, which is significantly lower.
+
+We would also like to point out the case of China Southern Airlines and China Eastern Airlines.
+Looking at only the diameter, we can conclude that the Network is as large as United or Delta Airlines.
+But when we look at the mean, they are only around 1400 km, which represent airlines like Ryanair or Southwest Airlines.
+This discrepancy can be explained by analyzing the median geometric distance of these networks.
+These Chinese Airlines have a median of around 1100 km, which means they have a lot of routes which are within China region only. 
+And looking at the full network, we can also say that, the main reason their diameter is over 12000 km is because they had recently started to offer few routes to countries like Canada, United States and Germany.
+Although these are large distances, due to high number of local routes within China, the mean route length of this network, turns out to be much more lesser and comparable to Low Cost Carriers.
 
@@
 
-\section{Airline Cooperation Portential}
+\begin{figure}
+        \centering
+        \includegraphics[width=80mm]{imgs2/results/eigenvector_centrality_distribution.png}
+        \caption{
+Eigenvector Centrality Distribution}
+        \label{fig:eigen_distr}
+\end{figure}
+
+\begin{figure}
+        \centering
+        \includegraphics[width=80mm]{imgs2/results/closeness_centrality_distribution.png}
+        \caption{
+Closeness Centrality Distribution}
+        \label{fig:closeness_distr}
+\end{figure}
+
+\begin{figure}
+        \centering
+        \includegraphics[width=80mm]{imgs2/results/geometrical_distance_distribution.png}
+        \caption{
+Geometrical Distance Distribution}
+        \label{fig:geometric_distr}
+\end{figure}
+
+Figure~\ref{fig:geometric_distr} provides us the geometric route distance distribution for airlines United, Lufthansa, Ryanair and Southwest.
+Here too, there is an apparent distinction between the Full Service Airlines and the Low Cost Carriers.
+Ryan Air and Southwest offer so many routes around 1000 km range, that the peak of their distribution is also around that value.
+And of course, their routes stop at a maximum distance of around 4000 km. 
+Looking at the Full Service Carriers, though the global peak of the distribution of United and Lufthansa is also around the same distance of 1000 km, we can see that there is a second small peak at around 6000 km.
+This is nothing but the average route distance for Transatlantic flights between United States and Europe.
+Both of these airlines offer a considerable number of these routes, that it shows in the distribution curve distinctly.
+
+The centrality distributions (both eigenvector and closeness) of these four airlines also provide us with deep insights into their route network. 
+We see that in both the Figures~\ref{fig:eigen_distr} and ~\ref{fig:closeness_distr}, Ryan Air and Southwest have more airports with higher centrality value.
+We could say that the centrality of their network is distributed across many airports, instead of relying on few airports with really high centrality values. 
+The scenario of having few airports with really high centrality value is seen in the case of Full Service Airlines Lufthansa and United Airlines.
+They have high number of airports with low centrality, and few select airports with high centrality values.
+If we look at the network diagram that was previously shown in Figure~\ref{fig:united_airline}, it is apparent that these high centrality airports are basically the hubs of these networks.
+
+\section{Airline Cooperation Potential}
 
@@
 "The connection and navigation times within the hub airport are shorter and the hassle is less than with a change of carrier" \cite{airline_consolidation_and_consumer_welfare}. 
-Think for example about the hassle that arises if you have booked two segments independently and you miss the seccond flight due to a delay of the first flight.
+Think for example about the hassle that arises if you have booked two segments independently and you miss the second flight due to a delay of the first flight.
 
@@
 
-We construct a simple but powerfull metric that captures this welfare gain for a potential merge of two airlines $l$ and $m$.
+We construct a simple but powerful metric that captures this welfare gain for a potential merge of two airlines $l$ and $m$.
 
@@
  & \Largeness_{2}(l) = \\
-= & \displaystyle\sum_{p,r \in P,\exists_{q}: pql \in E \and qrl \in E}: \sqrt(\patronage(p) * \patronage(r))
+= & \displaystyle\sum_{\substack{p,r \in P \\ \exists_{q}: pql \in E \and qrl \in E}}: \sqrt(\patronage(p) * \patronage(r))
 \end{aligned}
@@
 & \Potential(l,m) = \\
-= & \dfrac{\Largeness_{2}(l \cup m)}{\Largeness_{2}(l) + \Largeness_{2}(m)} 
+={} & \dfrac{\Largeness_{2}(l \cup m)}{\Largeness_{2}(l) + \Largeness_{2}(m)} 
 \end{aligned}
@@
 We implemented an algorithm that merges one airline with another, until only $N$ are left.
-In each step, the two arilines $l$ and $m$ are merged, that have the highest $\Potential$.
+In each step, the two airlines $l$ and $m$ are merged, that have the highest $\Potential$.
 
@@
 It also does not operate much in Canada in both the generated and real alliances landscape.
-As expected, there are also differences: For example the generated alliance Landscape suggests spanish speaking South American Countries to be in the same alliance and have Brazilian oparators close to the green alliance, while in real life Buenos Aires is tied to the green alliance (Skyteam) while Brazil get's supplied by a mix of alliances.
-Japan for example belongs to Staralliance in the realworld while in the generated landscape it's a part of big green alliance.
+As expected, there are also differences: For example the generated alliance Landscape suggests Spanish speaking South American Countries to be in the same alliance and have Brazilian operators close to the green alliance, while in real life Buenos Aires is tied to the green alliance (Skyteam) while Brazil gets supplied by a mix of alliances.
+Japan for example belongs to Staralliance in the real world while in the generated landscape it's a part of big green alliance.
 
@@
 \section{Outlook: Improving the metric}
-The $\Largeness$ metric could be improved.
+The $\Largeness_{2}$ metric could be improved.
 Right now, when two airlines have the same 2-segment connections, after joining the network, those connections will be counted only once.
@@
 A very promising different approach to capturing welfare that arises from additional single-ticket multi-segment flights through a merger or cooperation between airlines, is to look at the sum of the product of the weighted eigenvector centralities of common airports of the two merge candidates.
-
-$\cap$
 
@@
 
+While reflecting about this new approach we were wondering about the correlation of eigenvalue and patronage.
+There is an interesting correlation as you can see in Figure~\ref{fig:patronage_eigenvector}.
+
+Thus, considering eigenvector of each airport and using it in a new metric could provide us with different results, from what we achieved through$\Largeness_{2}$ metric. 
+We should also look at the interactions in the network, from the side of airports. Airports also have a significant amount of bargaining power, since they rent their space to be used by the airlines.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=80mm]{imgs2/results/patronage_eigenvector.png}
+	\caption{
+	Patronage vs Eigenvector Distribution}
+\label{fig:patronage_eigenvector}
+\end{figure}
+
+In the real world, profit of each airlines also plays a major factor in the formation of alliances.
+The typical cost of the airlines are divided into three categories: Flight (Direct) Operating Costs as 50\%, Ground Operating Costs as 30\% and System Operating Costs as 20\%.
+\cite{airline_operating_cost}
+Out of the above three categories, Ground Operating Costs, are especially related to fees to be paid to airports such as aircraft landing fees and reservation charges. 
+Having a coalition with many airlines together, would increase the bargaining power of these alliances, and help in reducing the costs to be paid to these airports.
+
 \section*{Acknowledgments}
-We thank our professor IProf. Ph.D. konnikova and her Sofia Berdysheva for their brilliance, support and for giving this outstanding course at TUM.
+We thank our professor Prof. Ph.D. Ikonnikova and Sofia Berdysheva for their brilliance, support and for giving this outstanding course at TUM.
 

### 2020-02-19 analysis/allianceFormation.py
scripts for generating alliance and graphs

@@ -1,0 +1,116 @@
+import operator
+
+import networkx as nx
+import sqlite3
+import numpy as np
+
+
+def common(a, b):
+    c = [value for value in a if value in b]
+    return c
+
+
+def allianceForms(subG1, nodes1, centrality1, path2MatrixSum1, path3MatrixSum1, airlineId):
+    if len(airlineId) > 3:
+        signiFactor = {}
+        for i in range(0, len(airlineId)):
+            for j in range(i + 1, len(airlineId)):
+                x = 0
+                commonNodes = common(nodes1[airlineId[i]], nodes1[airlineId[j]])
+                for eachNode in commonNodes:
+                    x += centrality1[airlineId[i]][eachNode] * centrality1[airlineId[j]][eachNode]
+
+                combinedG = nx.DiGraph()
+                combinedG = nx.compose(subG1[airlineId[i]], subG1[airlineId[j]])
+                adjMat = nx.adjacency_matrix(combinedG).todense()
+                path2combinedG = np.matmul(adjMat, adjMat)
+                path3combinedG = np.matmul(path2combinedG, adjMat)
+                path2combinedSum = path2combinedG.sum()
+                path3combinedSum = path3combinedG.sum()
+                y = 0
+                y = path2combinedSum / (path2MatrixSum1[airlineId[i]] + path2MatrixSum1[airlineId[j]])
+                z = path3combinedSum / (path3MatrixSum1[airlineId[i]] + path3MatrixSum1[airlineId[j]])
+                signiFactor[i, j] = x * y + x * z
+
+        sorted_Alliances = sorted(signiFactor.items(), key=operator.itemgetter(1), reverse=True)
+        id1 = airlineId[sorted_Alliances[0][0][0]]
+        id2 = airlineId[sorted_Alliances[0][0][1]]
+        print(airlineId)
+        print(sorted_Alliances[0][0][0])
+        print(sorted_Alliances[0][0][1])
+        airlineId.pop(sorted_Alliances[0][0][0])
+        airlineId.pop(sorted_Alliances[0][0][1] - 1)
+        print(airlineId)
+        print("Alliance: ", id1)
+        print("And: ", id2)
+        print(str(id1) + str(id2))
[…]

### 2020-02-19 analysis/fullgraph.py

@@ -14,20 +14,37 @@ rows = cursor.fetchall()
 for row in rows:
     if not G.has_edge(row[3], row[5]):
         G.add_edge(row[3], row[5])
+
+
 # cursor.execute("SELECT * from airports")
 # rows = cursor.fetchall()
 # patronage = {}
 # for row in rows:
 #     patronage[row[0]] = row[15]
+
+centrality = nx.degree_centrality(G)
+print(centrality)
+degreeCentr = []
+for centr in centrality.values():
+    degreeCentr.append(centr)
+degree = []
+frequency = []
+counter = collections.Counter(degreeCentr)
+for item in counter.keys():
+    degree.append(item)
+    frequency.append(counter[item])
+plt.xscale('log')
+plt.yscale('log')
+plt.hist(degree, bins=np.linspace(0.0, 0.2, 200))
+plt.show()
+
+
+
+
+# pos = nx.spring_layout(G, scale=2)
+# nx.draw_networkx(G, pos, with_labels=True, arrows=False, alpha=0.2, node_size=1, font_size=0.1, width=0.1)
+# plt.savefig("unitedNetwork.png", bbox_inches='tight', format='png', dpi=300)
 #
-# centrality = nx.eigenvector_centrality(G)
-# print(centrality)
-
-
-pos = nx.spring_layout(G, scale=2)
-nx.draw_networkx(G, pos, with_labels=True, arrows=False, alpha=0.2, node_size=1, font_size=0.1, width=0.1)
-plt.savefig("unitedNetwork.png", bbox_inches='tight', format='png', dpi=300)
-
 
 # def llllamda(key):
 #     return patronage[key]

### 2020-02-19 paper/main.tex
final changes in latex

@@
 After cleaning up the data, there are 3139 airports. 
-Interpreting the data as a graph gives us a multi-edge directed graph).
+Interpreting the data as a graph gives us a multi-edge directed graph.
 Looking at the degree distribution in Figure~\ref{fig:degree_distribution}, the alternating characteristic of degrees strikes the eye.
@@
 Besides the main subgraph, that includes 3113 nodes, there are 6 small disconnected ones with only a couple of nodes.
-One with 10 nodes for example Figure~\ref{fig:new_caledonia}, consists only of airports that are located in New Caledonia, an archipelago in the Pacific Ocean. 
+One with 10 nodes for example, Figure~\ref{fig:new_caledonia}, consists only of airports that are located in New Caledonia, an archipelago in the Pacific Ocean. 
 \begin{figure}
@@
 For 1956 of the 3139 airports from the dataset, we can find patronage data from Wikidata.
-Get an impression about the regional differences of data availability by looking at the percentage of airports for which Wikidata yields a patronage in Table~\ref{tab:patr_av_most_airports} and Table~\ref{tab:patr_av_worst}.
+We can also get an impression about the regional differences of data availability, by looking at the percentage of airports for which Wikidata yields a patronage in Table~\ref{tab:patr_av_most_airports} and Table~\ref{tab:patr_av_worst}.
 \begin{table}[h]
@@
 \end{table}
-We need to distinguish between monthly and yearly values and we extrapolate 2014 data from close years in case no data for the year 2014. 
+We need to distinguish between monthly and yearly values and we extrapolate 2014 data from close years in case there is no data for the year 2014. 
 In order to populate the remaining nodes with reasonable patronages as well, we tried different techniques.
+
 First we used data about runway surfaces that we found on ourflights.org. 
-
 We summed up the surfaces of runways for every airport and then calculated the average ratio between total runway surface area and patronage of airports where both data points were present, in order to predict patronage for airports without patronage data but with runway surface data based on this average ratio.
 For the still remaining >1000 airports without patronage we would then apply a default value that equals the average of the smallest 1\% of airports with patronage data from Wikidata. 
-The runway data turned out to be very unclean and unreliably. Water runways and other quirks were distorting the predictions.
+The runway data turned out to be very unclean and unreliable. Water runways and other quirks were distorting the predictions.
 
 Inspired by Prof.
-Ikonnikova advice during the presentation we switched to estimating the remaining airport patronages by looking at neighboring airports with patronage data.
+Ikonnikova's advice during the presentation we switched to estimating the remaining airport patronages by looking at neighboring airports with patronage data.
 The Algorithm can be seen in Listing~\ref{lst:patronage_estimation_algorithm}.
-\begin{lstlisting}[language=Python, caption={Patronage estimation algorithm, that using neighboring airport's patronage data}, label=lst:patronage_estimation_algorithm]
+\begin{lstlisting}[language=Python, caption={Patronage estimation algorithm, that uses neighboring airport's patronage data}, label=lst:patronage_estimation_algorithm]
 G = loadEntireNetwork()
@@
 
-The flows are estimated by choosing reasonable initial values and then applying corrections iteratively to approach a situation where the sum of the estimated flows for each airport equal its patronage value.
+The flows are estimated by choosing reasonable initial values and then applying corrections iteratively to approach a situation where the sum of the estimated elows for each airport equal its patronage value.
 The average initial values for an edge between airport $p$ and $q$ is chosen as:
@@
 The ratios we choose here will stay intact over the course of the iterations in the next part of the algorithm.
-In every iteration, we traverse all airports and for every airport we calculate the sum of current flows values of all routes. 
+In every iteration, we traverse all airports and for every airport we calculate the sum of current flow values of all routes. 
 \begin{equation}
@@
 \end{equation}
-Difference between the patronage and the current sum of passenger flows of incoming and outgoing routes. 
 Then, for each airport we calculate the difference between its patronage and the current sum of flows.
@@
 \end{equation}
-it expresses how well the sum of estimated flows match the patronage, that we know for the airport.
+It expresses how well the sum of estimated flows match the patronage, that we know for the airport.
 If the flows are half the patronage the absolute value of $\flowDeviation$ will be the same as when the current flows are twice the actual patronage number.
@@
 The blue line shows the $\flowDeviation$ distribution of the initial flow values.
-The other lines show the $\flowDeviation$ distribution after a the first couple of iterations and after the final iteration. 
-In the case of patronage estimations based on neighboring airports, we see that the $\flowDeviation$ distribution after the 120th iteration comes very close to $y=0$ which is also reflected by the $sum(abs)$ in the legend which is the sum of the absolute value of $\flowDeviation$ over all airports which is $0.94$ in this case.
+The other lines show the $\flowDeviation$ distribution after the first couple of iterations and after the final iteration. 
+In the case of patronage estimations based on neighboring airports, we see that the $\flowDeviation$ distribution after the 120th iteration comes very close to $y=0$ which is also reflected by the $sum(abs)$ in the legend, which is the sum of the absolute value of $\flowDeviation$ over all airports which is $0.94$ in this case.
 
@@
 emphasize the importance of network effects for airline competition.
-The mention Carlton, Landes and Posner \cite{costs-and-benefits-of-airline-mergers}, who found out, that when there is an intermediate stop on a trip, consumer welfare is higher, if both segments are operated by the same airline.
+They mention Carlton, Landes and Posner \cite{costs-and-benefits-of-airline-mergers}, who found out, that when there is an intermediate stop on a trip, consumer welfare is higher, if both segments are operated by the same airline.
 "The connection and navigation times within the hub airport are shorter and the hassle is less than with a change of carrier" \cite{airline_consolidation_and_consumer_welfare}. 
@@
 
-To assess the potential of a merge $\Potential(l,m)$ we divide the Largeness of the joint airline network by the sum of the Largenesses of the separate airline networks.
+To assess the potential of a merge, we divide the Largeness of the joint airline network by the sum of the Largenesses of the separate airline networks.
 
@@
 
-Imagine the merge of two airlines yields many new 2-segment flight routes (look at the example in Figure~\ref{fig:potential-example}.
+Imagine the merge of two airlines yields many new 2-segment flight routes (look at the example in Figure~\ref{fig:potential-example}).
 If there is already a big overlap between the networks, $\Potential(l,m)$ might even be $< 1$ and thus discourage a merger or cooperation\footnote{this aspect of the $\Largeness$ metric might deserve criticism.
@@
 "Which alliance should airline X join?"
+
 "Which airlines should form alliances?"
@@
 We plot the result on a world map (Figure~\ref{fig:generated-alliance-map}) and compare it to the real alliance landscape (Figure~\ref{fig:real-alliance-map}.
-An remarkable similarity between the generated alliance landscape and the real one, is that one big alliance (green) is covering a lot of flights between the US, Europe and China, but is not much active in South America, South Africa, Australia or New Zealand.
+A remarkable similarity between the generated alliance landscape and the real one, is that one big alliance (green) is covering a lot of flights between the US, Europe and China, but is not much active in South America, South Africa, Australia or New Zealand.
 It also does not operate much in Canada in both the generated and real alliances landscape.
@@
 \section*{Acknowledgments}
-We thank our professor Prof. Ph.D. Ikonnikova and Sofia Berdysheva for their brilliance, support and for giving this outstanding course at TUM.
+We thank our professor Prof. Ikonnikova and Sofia Berdysheva for their brilliance, support and for giving this outstanding course at TUM.
 

### 2020-02-19 paper/main.tex
small corrections

--- 2020-02-19 paper/main.tex
@@
 
-\date{Received: 19.02.2020 - This is work in progress}
+\date{Handed in on 19.02.2020}
 
@@
 We propose one metric that plays a role in forecasting whether a cooperation between two airlines is advantageous and use this metric to generate an alliances landscape.
-We compare it's predictive correctness to the real world by looking at the formation of Vanilla Airlines which occurred in the year after the one our data stems from.
+We compare it's predictive correctness to the real world. 
+We criticise the proposed metric and present a different approach. 
 \end{abstract}
@@
 Initially, we would like to analyze the entire worldwide airline network, and provide some insights regarding the airline industry.
-Since a particular route could be provided by multiple Airline Companies, the final network that we come up with is a Multiple Directed Network.
-The attributes of each edge in this network included both the geometrical distance and the average passenger flow of that route (edge). 
-As we can see from the Table~\ref{Tab:distance_metrics}, the diameter of the entire network is given along with the Total Distance of the routes and the Average Distance of routes in a network.
+Since a particular route could be provided by multiple airline companies, the final network that we come up with is a multiple directed network.
+After enrichment the attributes of each edge in this network include both the geometrical distance and the average passenger flow of that route (edge). 
+As we can see from the Table~\ref{Tab:distance_metrics}, the diameter of the entire network is given along with the total distance of the routes and the average distance of routes in a network.
 
+\begin{table}[ht]	
 \begin{center}
-\begin{table}[ht]	
  \begin{tabular}{| c | c | c |}
@@
  \end{tabular}
-\caption{Distance Metrics of the Network in km}
+\caption{Distance metrics of the network in km}
 \label{Tab:distance_metrics}	 
+\end{center}
 \end{table}
-\end{center}
 
-We currently do not have the ability to calculate centrality parameters like Eigenvector, Closeness or betweenness Centrality for a Multidirected Graph.
-So we will be mainly looking at Degree Centrality of the entire network as shown in Figure~\ref{fig:degree_centrality}.
-This is because Degree Centrality is the only Centrality available for Multiple Directed Graphs.
+For a multi directed graph, most centrality measures except degree centrality (Figure~\ref{fig:degree_centrality}) are not defined.
 
@@
 
-Just by analyzing the graph, we can say that the degree centrality distribution is following the Power Law Distribution.
+However, a multi directed graph can be converted to a directed graph, by merging the edges.
+
+Just by analyzing the graph, we can say that the degree centrality distribution is following the power law distribution.
 
@@
 
-Airline Networks can be mainly divided into two different types of networks. Full Service Airlines which are also called as Legacy Carriers, and Low Cost Airlines or Low Cost Carriers.  
-Full Service Airlines generally provide free baggage allowance, meals, drinks, seat selection and in-flight entertainment at no extra charge.
-Low Cost Carriers will usually collect ancillary revenue for all or most of the above these amenities.
-Most of the time, Low Cost Carriers operate in a specific regions.
-These specific regions could be within countries, or within continents, or within specific part of the continents.
+Airline networks can be mainly divided into two different types of networks. Full service airlines which are also called legacy carriers, and low cost airlines or low cost carriers.  
+Full service airlines generally provide free baggage allowance, meals, drinks, seat selection and in-flight entertainment at no extra charge.
+Low cost carriers will usually collect ancillary revenue for all or most of the these amenities.
+Most of the time, low cost carriers operate in a specific regions.
+These specific regions could be within countries, within continents, or within specific parts of the continents.
 
@@
 For the long haul low cost carriers to survive and adapt, they must continue to innovate.
-Their business models should focus on three new emerging carrier types: Network, Product and Price Specialist, according to John G.Wensveen and Ryan Leick.\cite{long_haul_lcc_new_model}
+Their business models should focus on three new emerging carrier types: network, product and price Specialist, according to John G.Wensveen and Ryan Leick.\cite{long_haul_lcc_new_model}
 
 Before we look at the differences in the network parameters of these two types of airlines, there are major differences in the network architecture itself.
-While the major Full Service Airlines often have the Network Type of "Hub and Spoke", the Low Cost Carriers are known to have Point to Point Network Type, according to research by Cook G.N and Goodwin, J.\cite{airline_network_comparison}
+While the major full service airlines often have the network type of "Hub and Spoke", the low cost carriers are known to have "Point to Point" network type, according to research by Cook G.N and Goodwin, J.\cite{airline_network_comparison}
 This "Hub and Spoke" network connection can be seen in the network graph of United Airlines and American Airlines given in Figure~\ref{fig:united_airline} and Figure~\ref{fig:american_airline} respectively.
-These two airlines are prime example of Full Service Airlines.
+These two airlines are prime example of full service airlines.
 
-Similarly we see the "Point to Point" Network in Low Cost Carriers like Ryan Air in Figure~\ref{fig:ryan_air} and Southwest Airlines in Figure~\ref{fig:southwest_airline}.
+Similarly we see the "Point to Point" Network in low cost carriers like Ryan Air in Figure~\ref{fig:ryan_air} and Southwest Airlines in Figure~\ref{fig:southwest_airline}.
 
@@
         \caption{
-Network of Ryan Air}
+Network of Ryanair}
         \label{fig:ryan_air}
@@
 
-We can also appreciate these major differences by analyzing various parameters of the network.
-As shown in Table~\ref{Tab:distance_airlines}, we can see that the Full Service Airlines like United Airlines, American Airlines and Delta Airlines, offer routes over really long distances.
+We can also notice these major differences by analyzing various parameters for airline subgraphs.
+As shown in Table~\ref{Tab:distance_airlines}, we can see that the full service airlines like United Airlines, American Airlines and Delta Airlines, offer routes over really long distances.
 That is the reason why the geometric distance diameters of these airline networks are easily over 12000 km.
-On the other hand, Low Cost Carriers always offer routes within a certain region, such as only within Europe (Ryan Air) or only within United States (Southwest Airlines).
+On the other hand, low cost carriers offer routes within a certain region, such as within Europe (Ryan Air) or within the United States (Southwest Airlines).
 And as expected, the diameter of these airline networks are below 4000 km.
@@
 The differences are also apparent when we look at the mean geometric distance of all the routes offered by a particular airline.
-Full Service Carriers show an average route distance of around 2300 km, while the Low Cost Carriers show that their average route distance is about 1400 km, which is significantly lower.
+Full service carriers show an average route distance of around 2300 km, while the low cost carriers show that their average route distance is about 1400 km, which is significantly lower.
 
 We would also like to point out the case of China Southern Airlines and China Eastern Airlines.
-Looking at only the diameter, we can conclude that the Network is as large as United or Delta Airlines.
-But when we look at the mean, they are only around 1400 km, which represent airlines like Ryanair or Southwest Airlines.
+The diameter of those two airlines is as large as the one of United or Delta Airlines. 
+But when we look at the mean distances of the those two Chinese airlines, they are only around 1400 km, which is common for airlines like Ryanair or Southwest Airlines.
 This discrepancy can be explained by analyzing the median geometric distance of these networks.
@@
 And looking at the full network, we can also say that, the main reason their diameter is over 12000 km is because they had recently started to offer few routes to countries like Canada, United States and Germany.
-Although these are large distances, due to high number of local routes within China, the mean route length of this network, turns out to be much more lesser and comparable to Low Cost Carriers.
+Although these are large distances, due to the high number of local routes within China, the mean route length of this network, turns out to be much lesser and comparable to low cost carriers.
 
@@
  \end{tabular}
-\caption{Mean, Median and Diameter of subgraphs of major airlines (all numbers in kilometers)}
+\caption{Mean, median and diameter of subgraphs of major airlines (all numbers in km)}
 \label{Tab:distance_airlines}
@@
  \end{tabular}
-\caption{Passenger Flow of Major Airlines}
+\caption{Passenger flow of major airlines}
 \label{Tab:passenger_flow_airlines}
@@
         \caption{
-Eigenvector Centrality Distribution}
+Eigenvector centrality distribution}
         \label{fig:eigen_distr}
@@
         \caption{
-Closeness Centrality Distribution}
+Closeness centrality distribution}
         \label{fig:closeness_distr}
@@
         \caption{
-Geometrical Distance Distribution}
+Geometrical distance distribution}
         \label{fig:geometric_distr}
@@
 Figure~\ref{fig:geometric_distr} provides us the geometric route distance distribution for airlines United, Lufthansa, Ryanair and Southwest.
-Here too, there is an apparent distinction between the Full Service Airlines and the Low Cost Carriers.
-Ryan Air and Southwest offer so many routes around 1000 km range, that the peak of their distribution is also around that value.
+Here too, there is an apparent distinction between the full service airlines and the low cost carriers.
+Ryanair and Southwest offer so many routes around 1000 km range, that the peak of their distribution is also around that value.
 And of course, their routes stop at a maximum distance of around 4000 km. 
-Looking at the Full Service Carriers, though the global peak of the distribution of United and Lufthansa is also around the same distance of 1000 km, we can see that there is a second small peak at around 6000 km.
-This is nothing but the average route distance for Transatlantic flights between United States and Europe.
+Looking at the full service carriers, though the global peak of the distribution of United and Lufthansa is also around the same distance of 1000 km, we can see that there is a second small peak at around 6000 km.
+This is to a big extetent caused by transatlantic flights between United States and Europe.
 Both of these airlines offer a considerable number of these routes, that it shows in the distribution curve distinctly.
@@
 We could say that the centrality of their network is distributed across many airports, instead of relying on few airports with really high centrality values. 
-The scenario of having few airports with really high centrality value is seen in the case of Full Service Airlines Lufthansa and United Airlines.
-They have high number of airports with low centrality, and few select airports with high centrality values.
+The scenario of having few airports with really high centrality value is seen in the case of full service airlines Lufthansa and United Airlines.
+They have a high number of airports with low centrality, and a few select airports with high centrality values.
 If we look at the network diagram that was previously shown in Figure~\ref{fig:united_airline}, it is apparent that these high centrality airports are basically the hubs of these networks.
@@
 We plot the result on a world map (Figure~\ref{fig:generated-alliance-map}) and compare it to the real alliance landscape (Figure~\ref{fig:real-alliance-map}.
-An remarkable similarity between the generated alliance landscape and the real one, is that one big alliance (green) is covering a lot of flights between the US, Europe and China, but is not much active in South America, South Africa, Australia or New Zealand.
+An remarkable similarity between the generated alliance landscape and the real one, is that one big alliance (the green alliance) is covering a lot of flights between the US, Europe and China, but is not much active in South America, South Africa, Australia or New Zealand.
 It also does not operate much in Canada in both the generated and real alliances landscape.
-As expected, there are also differences: For example the generated alliance Landscape suggests Spanish speaking South American Countries to be in the same alliance and have Brazilian operators close to the green alliance, while in real life Buenos Aires is tied to the green alliance (Skyteam) while Brazil gets supplied by a mix of alliances.
-Japan for example belongs to Staralliance in the real world while in the generated landscape it's a part of big green alliance.
+As expected, there are also differences: For example the generated alliance Landscape suggests Spanish speaking South American Countries to be in the same alliance and have Brazilian operators that are mostly part of the green alliance, while in real life Buenos Aires is tied to the Skyteam while Brazil gets supplied by a mix of alliances.
+Japan for example belongs to Staralliance in the real world while in the generated landscape it's a part of the green alliance.
 
@@
 
-Thus, considering eigenvector of each airport and using it in a new metric could provide us with different results, from what we achieved through$\Largeness_{2}$ metric. 
-We should also look at the interactions in the network, from the side of airports. Airports also have a significant amount of bargaining power, since they rent their space to be used by the airlines.
-
 \begin{figure}
@@
 
-In the real world, profit of each airlines also plays a major factor in the formation of alliances.
-The typical cost of the airlines are divided into three categories: Flight (Direct) Operating Costs as 50\%, Ground Operating Costs as 30\% and System Operating Costs as 20\%.
-\cite{airline_operating_cost}
-Out of the above three categories, Ground Operating Costs, are especially related to fees to be paid to airports such as aircraft landing fees and reservation charges. 
-Having a coalition with many airlines together, would increase the bargaining power of these alliances, and help in reducing the costs to be paid to these airports.
+With more data and especially financial data, there are million ways to explore and develop comprehensive models for assessing alliance forming and cooperation potential.
+
+Also, the interplay between airlines and between airlines and airport operators could be investigated from a game theoretic perspective in future work.
 

### 2020-02-19 paper/main.tex

@@
 We propose one metric that plays a role in forecasting whether a cooperation between two airlines is advantageous and use this metric to generate an alliances landscape.
-We compare it's predictive correctness to the real world. 
-We criticise the proposed metric and present a different approach. 
+We compare it's predictive correctness to the real world, criticise it and present one promising further approach. 
 \end{abstract}
@@
 \begin{figure}[h]
-
 	\centering
@@
 
-\begin{table}[ht]
+\begin{table}[h]
 \begin{center}
@@
 We plot the result on a world map (Figure~\ref{fig:generated-alliance-map}) and compare it to the real alliance landscape (Figure~\ref{fig:real-alliance-map}.
-An remarkable similarity between the generated alliance landscape and the real one, is that one big alliance (the green alliance) is covering a lot of flights between the US, Europe and China, but is not much active in South America, South Africa, Australia or New Zealand.
+A remarkable similarity between the generated alliance landscape and the real one, is that one big alliance (the green alliance) is covering a lot of flights between the US, Europe and China, but is not much active in South America, South Africa, Australia or New Zealand.
 It also does not operate much in Canada in both the generated and real alliances landscape.
@@
 
-\begin{figure}
+\begin{figure}[t]
 	\centering
@@
 	\caption{
-	Patronage vs Eigenvector Distribution}
+	Patronage vs. eigenvector distribution}
 \label{fig:patronage_eigenvector}
@@
 \section*{Acknowledgments}
-We thank our professor Prof. Ph.D. Ikonnikova and Sofia Berdysheva for their brilliance, support and for giving this outstanding course at TUM.
-
+We thank Prof. Ikonnikova and Sofia Berdysheva for their inspiration, support and for giving this outstanding course at TUM. 
+\\\\\\\\\\\\\\\\\\\\\\\\\\\\
 \bibliographystyle{IEEEtran}
